---
title: "Mixed Effects Models: MPa, Pre- and Post-TLP"
author: "Joe Celebrezze"
date: "2023-01-10"
output: html_document
---

The following script was written in response to a peer editor's comments. The summary tables at the bottom cross-referenced with the segmented regression results further support our conclusion that water potential has more of a linear response with flammability metrics or proxies than any sort of TLP-driven thresholding response.

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(data.table)
library(tidyverse)
library(cowplot)
library(lmerTest)
library(psych)
#devtools::install_github("strengejacke/strengejacke")
library(strengejacke)
library(sjPlot) # table functions
library(sjmisc) # sample data
library(here)
select = dplyr::select
here = here::here
library(modelsummary)
filter = dplyr::filter
mutate = dplyr::mutate
library(nlme)
library(MetBrewer)
library(remef)
library(kableExtra)
```

Set global options for color palettes and themes: 

```{r}
th <- theme(panel.background = element_rect(fill='white', colour='black'), # Make background white and border black
          panel.grid.major = element_blank(),  # Hide major gridlines
          panel.grid.minor = element_blank())

th.spp.wrap <- theme(legend.position = "bottom", 
        strip.text = element_text(face = "italic", size = 12) +
  scale_color_manual(values=met.brewer("Morgenstern", 7)))

Morgenstern = list(c("#7c668c", "#b08ba5", "#dfbbc8", "#ffc680", "#ffb178", "#db8872", "#a56457"), c(7, 5, 4, 6, 3, 2, 1), colorblind=TRUE)
```

#------------------------------------
# 1. Data wrangling
Reading in dataframe
```{r}
scaled.mem.data.alldates.noNAs <- read.csv(here('processed-data', 'mem.data.subset.alldates.csv'))
```

Seasonal mins and maxs from 2016 - 2020:

https://www.sbbg.org/about/onsite-weather-station-live-fuel-moisture 

```{r}
adfa_min <- 55
adfa_max <- 110

ceme_min <- 55
ceme_max <- 140
```

### All dates datasets
```{r, message=FALSE, warning=FALSE, include=FALSE}
adfa.subset <- scaled.mem.data.alldates.noNAs  %>% 
  filter(spp == "ADFA") %>% 
  filter(ignition == "1")

ceme.subset <- scaled.mem.data.alldates.noNAs  %>% 
  filter(spp == "CEME") %>% 
  filter(ignition == "1")

adfa.subset.allignitions <- scaled.mem.data.alldates.noNAs  %>% 
  filter(spp == "ADFA")

ceme.subset.allignitions <- scaled.mem.data.alldates.noNAs %>% 
  filter(spp == "CEME")
```

### PV Curve Data
```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"))

pv_local <- pv_summary_df_timing %>% 
  filter(spp %in% c("ADFA", "CEME"))
#ADFA
##LFM
mean_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()
upr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()
lwr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()
##MPa
mean_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()
upr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr)) %>% 
  pull()
lwr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr)) %>% 
  pull()
# CEME
##LFM
mean_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()
upr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()
lwr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()
##MPa
mean_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()
upr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr)) %>% 
  pull()
lwr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

### Splitting by TLP
```{r}
adfa.subset.pre <- adfa.subset %>% 
  filter(mpa > mean_mpa_adfa)
adfa.subset.post <- adfa.subset %>% 
  filter(mpa < mean_mpa_adfa)

ceme.subset.pre <- ceme.subset %>% 
  filter(mpa > mean_mpa_ceme)
ceme.subset.post <- ceme.subset %>% 
  filter(mpa < mean_mpa_ceme)
```

# --------------------------------
# 2. Mixed Effects Models
### PC1
```{r}
# ADFA
adfa.pc1.mem.pre <- lmer(PC1 ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.pre)
adfa.pc1.mem.post <- lmer(PC1 ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.post)
adfa.pc1.mem.all <- lmer(PC1 ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset)

# CEME
ceme.pc1.mem.pre <- lmer(PC1 ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.pre)
ceme.pc1.mem.post <- lmer(PC1 ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.post)
ceme.pc1.mem.all <- lmer(PC1 ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset)
```

### PC2
```{r}
# ADFA
adfa.pc2.mem.pre <- lmer(PC2 ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.pre)
adfa.pc2.mem.post <- lmer(PC2 ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.post)
adfa.pc2.mem.all <- lmer(PC2 ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset)

# CEME
ceme.pc2.mem.pre <- lmer(PC2 ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.pre)
ceme.pc2.mem.post <- lmer(PC2 ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.post)
ceme.pc2.mem.all <- lmer(PC2 ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset)
```

### TTI
```{r}
# ADFA
adfa.tti.mem.pre <- lmer(tti ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.pre)
adfa.tti.mem.post <- lmer(tti ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.post)
adfa.tti.mem.all <- lmer(tti ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset)

# CEME
ceme.tti.mem.pre <- lmer(tti ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.pre)
ceme.tti.mem.post <- lmer(tti ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.post)
ceme.tti.mem.all <- lmer(tti ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset)
```

### FH
```{r}
# ADFA
adfa.fh.mem.pre <- lmer(fh ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.pre)
adfa.fh.mem.post <- lmer(fh ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.post)
adfa.fh.mem.all <- lmer(fh ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset)

# CEME
ceme.fh.mem.pre <- lmer(fh ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.pre)
ceme.fh.mem.post <- lmer(fh ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.post)
ceme.fh.mem.all <- lmer(fh ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset)
```

### FD
```{r}
# ADFA
adfa.fd.mem.pre <- lmer(fd ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.pre)
adfa.fd.mem.post <- lmer(fd ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.post)
adfa.fd.mem.all <- lmer(fd ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset)

# CEME
ceme.fd.mem.pre <- lmer(fd ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.pre)
ceme.fd.mem.post <- lmer(fd ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.post)
ceme.fd.mem.all <- lmer(fd ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset)
```

### GD
```{r}
# ADFA
adfa.gd.mem.pre <- lmer(gd ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.pre)
adfa.gd.mem.post <- lmer(gd ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset.post)
adfa.gd.mem.all <- lmer(gd ~ mpa.scaled + site + year.month + (1 | individual), data = adfa.subset)

# CEME
ceme.gd.mem.pre <- lmer(gd ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.pre)
ceme.gd.mem.post <- lmer(gd ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset.post)
ceme.gd.mem.all <- lmer(gd ~ mpa.scaled + site + year.month + (1 | individual), data = ceme.subset)
```

# -------------------------------
# 3. Summary Tables
## ADFA
```{r}
tab_model(adfa.pc1.mem.pre, adfa.pc1.mem.post, adfa.pc1.mem.all, adfa.pc2.mem.pre, adfa.pc2.mem.post, adfa.pc2.mem.all, adfa.tti.mem.pre, adfa.tti.mem.post, adfa.tti.mem.all, adfa.fh.mem.pre, adfa.fh.mem.post, adfa.fh.mem.all, adfa.fd.mem.pre, adfa.fd.mem.post, adfa.fd.mem.all, adfa.gd.mem.pre, adfa.gd.mem.post, adfa.gd.mem.all,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE,
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         string.pred = "Coeffcient", 
         dv.labels = c("PC1 (pre-TLP)", "PC1 (post-TLP)", "PC1 (all)",
                       "PC2 (pre-TLP)",  "PC2 (post-TLP)", "PC2 (all)",
                       "TTI (pre-TLP)", "TTI (post-TLP)", "TTI (all)",
                       "FH (pre-TLP)",  "FH (post-TLP)", "FH (all)",
                       "FD (pre-TLP)", "FD (post-TLP)", "FD (all)",
                       "GD (pre-TLP)",  "GD (post-TLP)", "GD (all)"),
         title = "A. fasciculatum: MEM, Testing pre- and post-TLP",
  string.p = "P-Value", 
  p.style = "stars")
```

## CEME
```{r}
tab_model(ceme.pc1.mem.pre, ceme.pc1.mem.post, ceme.pc1.mem.all, ceme.pc2.mem.pre, ceme.pc2.mem.post, ceme.pc2.mem.all, ceme.tti.mem.pre, ceme.tti.mem.post, ceme.tti.mem.all, ceme.fh.mem.pre, ceme.fh.mem.post, ceme.fh.mem.all, ceme.fd.mem.pre, ceme.fd.mem.post, ceme.fd.mem.all, ceme.gd.mem.pre, ceme.gd.mem.post, ceme.gd.mem.all,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE,
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         string.pred = "Coeffcient",
         dv.labels = c("PC1 (pre-TLP)", "PC1 (post-TLP)", "PC1 (all)",
                       "PC2 (pre-TLP)",  "PC2 (post-TLP)", "PC2 (all)",
                       "TTI (pre-TLP)", "TTI (post-TLP)", "TTI (all)",
                       "FH (pre-TLP)",  "FH (post-TLP)", "FH (all)",
                       "FD (pre-TLP)", "FD (post-TLP)", "FD (all)",
                       "GD (pre-TLP)",  "GD (post-TLP)", "GD (all)"),
         title = "C. megacarpus: MEM, Testing pre- and post-TLP",
  string.p = "P-Value", 
  p.style = "stars")
```
