---
title: "Metadata"
author: "Joe Celebrezze and Indra Boving"
date: "2023-01-25"
output:
   html_document:
    toc: true
    toc_depth: 4
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
here = here::here
library(tidyverse)
```

Questions/concerns:
- should we redo 'sample' so that the numbering system is consistent for different sampling efforts?
- does all code run with latest removals of columns and datasets?

# Introduction

This .Rmd file covers the necessary metadata for the datasets that we used in the analyses for the paper, *Live fuel moisture and shoot water potential exhibit contrasting relationships with leaf-level flammability thresholds during laboratory flammability tests*.

It does so by describing each column of each dataset included in this GitHub. For more information on the organization of the GitHub or which scripts are responsible for which analyses, see the README file included on the GitHub. Many variables/columns are repeated on multiple datasets, and in these cases we do not describe them again, as this would be redundant; however, we try to make it clear where repeated columns exist and why.

This metadata was last updated on:
**February 22, 2023** by **Joe Celebrezze**

--------------------------

# Raw Data

## flam.local.alldates.csv
```{r, include = F}
flam.local.alldates <- read_csv(here("raw-data", "flam.local.alldates.csv"))
head(flam.local.alldates)
```

This dataframe contains n=795 observations of flammability tests on 'local species' (i.e., species sampled from the chaparral at the foothills of the Santa Ynez mountains in Santa Barbara county) and accompanying data on water status and content along the benchtop drydown.

*sample*: the identification number for the individual. Due to the uneven sampling regime over the duration of this experiment, the identification number differs slightly for different years. For more recent sampling, the identification number carries information about both the site and the individual in the format (site.individual or site.pod, see *pod* below); however in certain years, only site 1 was sampled from and in these cases the identification number only carries information about the individual in either of the following formats: for individual 3, *sample* = 3.0 or *sample* = 3.

*round*: this describes the order in which the samples were burned over the course of a laboratory drydown (i.e., round = 1 means the first sample of that particular individual that we burned)

*spp*: an abbreviation for the species tested (CEME = *Ceanothus megacarpus* and ADFA = *Adenostoma fasciculatum*)

*model*: an identifier of the method used (EPI = epiradiator and HP = hot plate; for this study, we solely used epiradiator)

*mpa*: water potential (-MPa), reported here as a positive number but changed to negative values in the data wrangling step

*lfm*: live fuel moisture (LFM, %), as measured using the following equation, taken on a subsample directly before testing flammability
\begin{equation}
LFM = 100 \times \frac{fresh weight - dry weight}{dry weight}
\end{equation}

*lfm.notes*: any notes taken on the live fuel moisture sample

*fh*: the maximum flame height (cm) observed during combustion

*ttfg*: time to first glow (seconds); time elapsed between loading the sample into the flammability chamber and the beginning of the glow time

*gti*: glow to ignition (seconds); time elapsed between beginning of glow time and the time which ignition occurred

*tti*: time to ignition (seconds); time elapsed between loading the sample into the flammability chamber and the time which ignition occurred

*fd*: flame duration (seconds); duration of the combustion from ignition to extinction of the flame

*gd*: glow duration (seconds); time elapsed between beginning and end of glow time

*pfg*: post-flame glow (seconds); time elapsed between extinction of flame (end of comubstion) and end of glow time

*ignition*: binary identifier describing whether or not the sample ignited (1 = ignited, 0 = not ignited)

*start.temp*: starting temperature (degrees Celsius) as measured by the thermocouple located 1 cm above the sample 

*temp.max*: maximum temperature (degrees Celsius) as measured by the thermocouple located 1 cm above the sample

*ignition.temp*: temperature (degrees Celsius) at the point of ignition as measured by the thermocouple located 1cm above the sample 

*prop.new*: estimated proportion of new growth in the sample as observed directly prior to loaading the sample in the flammability chamber

*sample.wt*: weight (g) of the sample loaded into the flammability chamber

*glow*: binary identifier describing whether or not the sample glowed (1 = glowed, 0 = did not glow)

*year*: identifier of year when we ran flammability tests in format YYYY

*month*: identifier of month, written out with a capital letter to start, when we ran flammability tests

*dry.wt*: the weight (g) after oven-drying for 24hr at 100C from the subsample used to measure live fuel moisture

*fresh.wt*: the weight (g) of the subsample used to measure live fuel moisture prior to oven-drying

*water.wt*: the difference between the *fresh_wt* and the *dry_wt* representing the weight of water (g) in the LFM subsample

*site*: a character identifier describing the site that we gathered the samples from (either St. Marys = chapparal Site 1 = 34.4613, -119.6934 or Painted Caves = chapparal Site 2 = 34.4931, -119.7910)

## local_field_data.csv
```{r, include = F}
local_field_data <- read_csv(here("raw-data", "local_field_data.csv"))
head(local_field_data)
```

This dataframe contains field data on 36 samples (2 species, 12 individuals, split *A. fasciculatum* into old and new growth, see *age*) on 9/18/20. This field data includes live fuel moisture measurements, predawn and midday water potential measurements and information regarding each species' turgor loss point (based on pressure-volume curves)

*bottle.number*: identifier for the label on the nalgene bottles which we placed live fuel moisture samples in during collection; each bottle had slightly different weights that we measured prior to collecting samples, thus the bottle.number was important information to include

*spp*: see above

*age*: New = growth from the last year, Old = growth from over a year ago; only *A. fasiculatum* was able to be confidently split by *age*

*pod*: the individual plant we sampled from; we labelled this as *pod* since we sampled *A. fasciculatum* and *C. megacarpus* individuals that were close together (i.e., from pod 1, both speccies were relatively close to each other, but they could be distant from the individuals we sampled from from pod 3)

*site*: see above

*lfm*: see above; for the field measurements, we took larger samples from healthy, sun-exposed leaves around solar noon, taking special care to avoid reproductive structures

*date*: date of collection in the following format M/DD/YY; in this case, all samples were collected on 9/18/2020

*predawn1* and *predawn2*: for each individual, we took two predawn water potential measurements, reported as a positive value of MPa (although, technically all values should be negative); note that we did not separate old and new growth for water potential measurements

*midday1* and *midday2*: like *predawnX* columns, we took two midday water potential measurements, around solar noon (concurrent with LFM sampling), again reported as positive values of MPa

*predawn* and *midday*: the average values of the *predawn1* and *predawn2* and *midday1* and *midday2* values (respectively)

*type*: functional group, split into shrubs and trees; however, for this dataset, both species are shrubs, so this column is not particularly useful in this case

*LFMtlp*: from pressure-volume curves (see *processed-data* > *pv_summary_df_timing.csv* for more information), this represents the live fuel moisture measurement at the turgor loss point

*Mpatlp*: from pressure-volume curves, this represents the water potential at the turgor loss point

## Precip_SBBG.csv
```{r, include = F}
Precip_SBBG <- read_csv(here("raw-data", "Precip_SBBG.csv"))
head(Precip_SBBG)
```

This dataset includes the daily precipitation values from a weather station near the Santa Barbara Botanic Gardens (*station id* = 321) from 1944-2020. This data was accessed at: https://www.countyofsb.org/2256/Historical-Rainfall-Reservoir-Informatio .

*station id*: identifier for the weather station used to measure daily precip.; in our case, we filtered out station id 321 prior to loading this dataset, so this is the only station present

*water year*: identifier of the year that precipitation data was gathered, based on the cycle of wet and dry seasons in Santa Barbara county rather than the traditionally used Gregorian calendar. This means that the start of the *water year* is around September or August, when thee dry season comes to a close rather than January  (e.g., October 2014 would be *water year* 2015 and *year* 2014).

*year*: identifier of the year that the precipitation data was gathered based on the traditional Gregorian calendar

*month*: identifier of the month that the precipitation data was gathered

*day*: identifier of the date that the precipitation data was gathered

*daily rain*: the amount of precipitation (inches) on the given date (based on *year* or *water year*, *month*, and *day*)

# Processed Data

In many cases, these are different iterations of wrangling *flam.local.alldates.csv* as done in *1.0_data_wrangling.Rmd* in which the columns will be repeated across different datasets and will only be described if they have not ben described before. However, the first two datasets that follow are not wrangled versions of *flam.local.alldates.csv* and, thus, will be described in more detail.

## precip.clean.csv
```{r, include = F}
precip.clean <- read_csv(here("processed-data", "precip.clean.csv"))
head(precip.clean)
```

This dataset is an alteration of *Precip_SBBG.csv* and it includes only the dates necessary to estimate the precipitation 2 months prior to sample collection dates.

*...1*: identifier of the row, used in data wrangling

*year*, *water.year*, and *day*: see above *year*, *water year*, and *day*

*year.month*: an identifier of the year and month in the format YYYY_MM

*daily.rain*: see above *daily rain*; daily precipitation in inches

*rainfall.2mo*: a sum of the daily rain values for the two months prior to sampling (which is denoted by *timing* as seen below)

*timing*: the month and year of sample collection in the following format Month_YYYY where 'Month' is formatted as a capitalized standard acronym of the sampling month (e.g. September 2020 = Sept_2020)

## pv_summary_df_timing.csv
```{r, include = F}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"))
head(pv_summary_df_timing)
```

This dataset contains necessary information from the pressure-volume curves that we conducted. From the methods section of the paper:

For turgor loss point estimation, pressure-volume curves were created for each species (Tyree & Hammel 1972). For both species, healthy 20-40 cm branches were collected from 6 individuals. Samples were processed within 1 hour after sample collection or were stored in a refrigerator at 4 C between processing if not processed immediately (maximally 6 hours after collection). For processing, branches were cut underwater into smaller branchlets and were rehydrated in darkness for 2 hours, after which healthy non-necrotic small leafy shoots were excised from the branch using a razor blade. To avoid the effects of oversaturation, care was taken to remove leaves and stems that had been underwater during rehydration (Meinzer et al., 2014).

Pressure-volume curves were created for 3-6 rehydrated leaves or shoots (1 per individual) using a Scholander pressure chamber. Consecutive water potential and weight measurements were taken on each leaf until three to five points of the linear section of the curve was reached as determined by maximizing the linear fit (R2). The LFM at the TLP (LFMTLP) was determined using the corresponding water content at the TLP in the pressure-volume curves. All pressure-volume curve parameters were determined using the protocols available on Prometheus wiki.

This dataset contains data gathered from the pressure-volume curves conducted on eight species, although only *Adenostoma fasciculatum* (ADFA) and *Ceanothus megacarpus* (CEME) are of interest for this paper.

*spp*: a species identifier following these abbreviations: ARPA = *Arctostaphylos patula*, ABCO = *Abies concolor*, CADE = *Calocedrus decurrens*, CECO = *Ceanothus cordulatus*, PIJE = *Pinus jeffreyii*, QUKE = *Quercus kelloggii*, and then *most importantly*: CEME = *Ceanothus megacarpus* and ADFA = *Adenostoma fasciculatum*

*timing*: the season that the PV curves were completed

*mean_tlp*: the average of the turgor loss point (TLP) across individuals tested (MPa)

*lwr*: the lower bounds of the TLP (MPa) as identified by subtracting one standard deviation from the TLP

*upr*: the upper bounds of the TLP (MPa) as identified by adding one standard deviation from the TLP

*mean_lfm*: the average of the TLP across individuals tested expressed as live fuel moisture (%); note that we did not do this for spring PV curves

*lwr_lfm*: the lower bounds of the TLP (LFM, %) as identified using by subtracting one standard deviation from the TLP (expressed as LFM)
 
*upr_lfm*: the upper bounds of the TLP (LFM, %) as identified using by adding one standard deviation from the TLP (expressed as LFM)

## local_flam_data_all.csv
```{r, include = F}
local_flam_data_all <- read_csv(here("processed-data", "local_flam_data_all.csv"))
head(local_flam_data_all)
mean(local_flam_data_all$round)
```

*individual*: an identifier for the individual which includes the date (YYYY_month), model (EPI = epiradiator), species (CEME = *Ceanothus megacarpus* and ADFA = *Adenostoma fasciculatum*), 10% bin of LFM (see *gr*), and a identification number for the individual

*model.spp.gr.sample*: duplicate column of *individual*
REMOVE? Done

note: there are other columns towards the left of this dataset not described here, as they can be more adequately explained after explaining some other columns, so they are pushed to the bottom of this list. Sorry for any confusion this may cause.

*sample*, *round*, *spp*, *model*, *mpa*, *lfm*, *lfm.notes*,: see *flam.local.alldates.csv* above

All *flammability metrics* are described in *flam.local.alldates.csv* above (*fh*, *ttfg*, *gti*, *tti*, *fd*, *gd*, *pfg*, *ignition*, *start.temp*, *temp.max*, *ignition.temp*, and *glow*)

*prop.new*, *sample.wt*, *year.month*, *year*, *month*, *dry.wt*, *fresh.wt*, *water.wt*, *site*: all described above in *flam.local.alldates.csv*

*lfm.outliers.out*: a column reporting LFM values, with outliers replaced with NAs

*lfm.NAs.imputed*: a column reporting LFM values, with NAs replaced by imputing the predicted LFM value at that water potential

*temp.change*: the difference between the starting temperature and the maximum temperature as identified by this equation:
\begin{equation}
temp.change = temp.max - start.temp
\end{equation}

*gr*: represents the 10% bin of LFM that the sample fell into (e.g., (90,100] = the sample's LFM was greater than 90% and less than or equal to 100%)

*precip.2month*: month used when accessing precipitation data (essentially a duplicate column of year_month)

*precip.2mo*: the precipitation (inches) recorded by a weather station at Santa Barbara Botanical Gardens for Santa Barbara county for the 2 months prior to flammability testing (see: https://www.countyofsb.org/2256/Historical-Rainfall-Reservoir-Informatio)

*season*: an identifier of whether or not sampling efforts occurred after (season = Wet) the beginning of seasonal rains (typically in the late fall to spring) or before (season = Dry) seasonal rains (typically late spring or early summer to late fall)

*prop.ignite*: denotes the proportion of samples that ignited per 10% bin of LFM (i.e., *gr*)

*bins5lfm_gr*: represents the 5% bin of LFM that the sample fell into

*individual.bins5lfm_gr*: an identifier of individual with *year*, *month*, *model*, *species*, and *bins5lfm_gr* preceding the individual id with an underscore between each of them

*prop.ignite.bins5*: denotes the proportion of samples that ignited per 5% bin of LFM (i.e., *bins5lfm_gr*); specific to sampling date, so that proportion ignited is only calculated from one round of flammability tests

*individual.bins5lfm_gr_nodate*: *individualbins5lfm_gr* without any information regarding *year* or *month*

*prop.ignite.bins5_nodate*: denotes the proportion of samples that ignited per 5% bin of LFM (i.e., *bins5lfm_gr*); this column is not specific to sampling date, so it uses the LFM bins and calculates proportion ignited based on all rounds of flammability tests for that given LFM bin

*bins10lfm_gr*: repeated column of *gr*

*individual.bins10lfm_gr_nodate*: *individual.bins10lfm_gr* (see below) without any information regarding *year* or *month*

*prop.ignite.bins10_nodate*: denotes the proportion of samples that ignited per 10% bin of LFM (i.e., *bins10lfm_gr* or *gr*); this column is not specific to sampling date, so it uses the LFM bins and calculates proportion ignited based on all rounds of flammability tests for that given LFM bin

*hydration*: an identifier denoting the hydration status of the sample based on LFM, split into "dry" (0-60% LFM), "moderate" (60-90% LFM), and "hydrated" (>90% LFM)

*bins5lfm*: duplicate column of *bins5lfm_gr*
REMOVE? Done

*bins10lfm*: duplicate column of *gr* and *bins10lfm_gr*
REMOVE? Done

*bins20lfm_gr*: represents the 20% bin of LFM that the sample fell into

*gdw.gfw*: grams of dry weight per grams of fresh weight (from LFM subsample); used in calculation of *dw.flam.sample* (see below)

*gww.gdw*: grams of wet weight per grams of dry weight (from LFM subsample)

*gdw.gww*: grams of dry weight per grams of wet weight (from LFM subsample)

*dw.flam.sample*: an estimate of the dry weight in the sample loaded into the flammability chamber derived from the *sample.wt* and the metrics that were used to calculate live fuel moisture (of a subsample collected at the same time as the flammability sample) (*dry.wt* and *fresh.wt*); this was used extensively in analyses and was calculated using this equation
\begin{equation}
sample.wt \times \frac{dry.wt}{fresh.wt}
\end{equation}
or
\begin{equation}
sample.wt \times gdw.gfw
\end{equation}

*ww.flam.sample*: an estimated of the water weight in the sample loaded into the flammability chamber; this was used often in analyses and was calculated using this equation 
\begin{equation}
sample.wt - dw.flam.sample
\end{equation}

*...outs*: the eight columns that all end with '.outs' are metrics described above but where certain datapoints are removed after being identified as outliers using the function outlierKD2 which was sourced from http://goo.gl/UUyEzD

*flam.index*: derived from Essaghi et. al. 2017, using maximum *tti* and maximum *fh*, an index of flammability as a scale of least (1) to most (20) flammable. The following equation was used: 
\begin{equation}
flam.index = x \times (\frac{max(tti) - tti}{min(tti) + tti})^{\frac{fh}{fh + max(fh)}^2}
\end{equation}
where max(tti), min(tti), and max(fh) were determined prior to calculating and where x is some arbitrary coefficient so that the maximum value off the flammability index (i.e., tti = 0, fh = max(fh)) is equal to 20

*mean.wt*: the mean sample weight (g) per species

*dry.norm...*: the seven columns -- *dry.norm.fh*, *dry.norm.gd*, *dry.norm.fd*, *dry.norm.pfg*, *dry.norm.ttfg*, *dry.norm.tti*, *dry.norm.gti* -- are the flammability metrics normalized by the dry weight of the flammability sample, as reported in *dw.flam.sample*; these were used in some exploratory analyses, but not very extensively

Returning to columns earlier in the dataset that I mentioned in the note above

*model.spp.bins5lfm_gr.sample*: duplicate column of *individual.bins5lfm_gr*
REMOVE? Done

*model.spp.bins5lfm_gr.sample_nodate*: duplicate column of *individual.bins5lfm_gr_nodate*
REMOVE? Done

*model.spp.bins10lfm_gr.sample_nodate*: duplicate column of *individual.bins10lfm_gr_nodate*
REMOVE? Done

*year.month.spp*: column with *year.month* and *spp* with an underscore separating the two

*model.spp.gr*: an identifier which includes *year.month*, *model*, *spp*, and *gr* separated by underscores
Is this duplicate? REMOVE?

*model.spp.bins5lfm_gr*: an identifier which includes *year.month*, *model*, *spp*, and *bins5lfm_gr* separated by underscores

*model.spp.bins5lfm_gr_nodate*: *model.spp.bins5lfm_gr* but without any information regarding *year* or *month*

## mem.data.local.epi.csv
Removed for now
```{r, include = F}
#mem.data.local.epi <- read_csv(here("processed-data", "mem.data.local.epi.csv"))
#head(mem.data.local.epi)
```

## mem.data.local.epi.2020.csv
```{r, include = F}
#mem.data.local.epi.2020 <- read_csv(here("processed-data", "mem.data.local.epi.2020.csv"))
#head(mem.data.local.epi.2020)
```
REMOVED FOR NOW. SEE IF NEEDED AT END


## mem.data.local.epi.alldates.csv
```{r, include = F}
mem.data.local.epi.alldates <- read_csv(here("processed-data", "mem.data.local.epi.alldates.csv"))
head(mem.data.local.epi.alldates)
```

This dataset was wrangled in the *2_PCA.Rmd* script, as the principal components were added to the dataset to be analyzed in the linear mixed effects models. Almost all of the columns have been described above and will not be described below. The following columns were not described anywhere above or require further clarification:

*PC1*, *PC2*, *PC3*, *PC4*, *PC5*, *PC6*, *PC7*, *PC8*: principal component values from the principal component analysis run on *2_PCA.Rmd*

*LFM*: live fuel moisture (%) as described in *lfm* above

## mem.data.subset.alldates.csv
```{r, include = F}
mem.data.subset.alldates <- read_csv(here("processed-data", "mem.data.subset.alldates.csv"))
head(mem.data.subset.alldates)
```

This dataset was created at the bottom of *1.0_data_wrangling.Rmd* as a wrangled version of *mem.data.local.epi.alldates.csv* and includes only the most important columns and also removes any samples with a weight outside of the range of 0.4-0.6g, thus it is a 43x447 dataframe rather than a 85x555 dataframe

*Species*: a species identifier using the first letter of the genus and the specific epiphet (e.g., A. fasciculatum)

*id*: see *individual* above

*timing*: see *timing* in precip.clean.csv above

*mpa.scaled*: scaled water potential using scale() function

*excess.water.unscaled*: excess water was determined using the following equation:
\begin{equation}
excess water = wet weight - dry weight
\end{equation}
where wet weight = *ww.flam.sample* and dry weight = *dw.flam.sample*  

*excess.water.scaled*: scaled *excess.water.unscaled* using the scale() function

*lfm*: in this case, this represents the scaled live fuel moisture using scale() function

*...unscaled*: any columns with this suffix represent the unscaled variable that precedes the suffix, which have all been described above

## seg.reg.data.local.csv
```{r, include = F}
seg.reg.data.local <- read_csv(here("processed-data", "seg.reg.data.local.csv"))
head(seg.reg.data.local)
```

This dataframe was created at the bottom of *1.0_data_wrangling.Rmd* as a wrangled version of *mem.data.local.epi.alldates.csv* and includes only the most important columns for the segmented regression analyses; like *mem.data.subset.alldates.csv*, it removes outliers of sample weights (outside range of 0.4-0.6g)

*lfm*: in this case, the column is equivalent to *lfm.NAs.imputed*, as any NA values would have thrown off the segmented regression analysis
