---
title: "Segmented Regressions - Mixed Effects Models"
author: "Indra Boving & Joe Celebrezze"
date: "4/15/2021"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
library(lubridate)
library(plotrix)
filter = dplyr::filter 
here = here::here
#source(here("source-code", "source-segmented.lme.R"))
```

# Reading in Dataframe
```{r}
seg.data.subset <- read.csv(here('processed-data', 'seg.reg.data.local.csv'))

seg.data.subset <- seg.data.subset %>% 
  na.omit()
```

# Color by Season
```{r}
seg.data.subset$color <- 'black'

seg.data.subset$color[seg.data.subset$year.month=='2020_September']="#c1121f"
seg.data.subset$color[seg.data.subset$year.month=='2020_January']="#64A400"
seg.data.subset$color[seg.data.subset$year.month=='2019_December']="#669BBC"
seg.data.subset$color[seg.data.subset$year.month=='2018_January']="#FF7262"
seg.data.subset$color[seg.data.subset$year.month=='2016_December']="#A4A7DE"
```

# Splitting by Species
```{r}
seg.ceme.subset <- seg.data.subset %>% 
  filter(spp == "CEME")
```

```{r}
seg.adfa.subset <- seg.data.subset %>% 
  filter(spp == "ADFA")
```

# Splitting by Sampling Date
```{r}
seg.ceme.s20.subset <- seg.ceme.subset %>% 
  filter(year.month == "2020_September")

seg.ceme.d19.subset <- seg.ceme.subset %>% 
  filter(year.month == "2019_December")

seg.adfa.s20.subset <- seg.adfa.subset %>% 
  filter(year.month == "2020_September")

seg.adfa.d16.subset <- seg.adfa.subset %>% 
  filter(year.month == "2016_December")
```


# Maximums for LFM, MPa
```{r}
max.lfm <- max(seg.data.subset$lfm)
max.mpa <- max(seg.data.subset$mpa)

max.lfm.c <- max(seg.ceme.subset$lfm)
max.mpa.c <- max(seg.ceme.subset$mpa)

max.lfm.a <- max(seg.adfa.subset$lfm)
max.mpa.a <- max(seg.adfa.subset$mpa)
```

# PV Curve Data
```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"))

pv_local <- pv_summary_df_timing %>% 
  filter(spp %in% c("ADFA", "CEME"))
#ADFA
##LFM
mean_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()
upr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()
lwr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()
##MPa
mean_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()
upr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr)) %>% 
  pull()
lwr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr)) %>% 
  pull()
# CEME
##LFM
mean_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()
upr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()
lwr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()
##MPa
mean_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()
upr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr)) %>% 
  pull()
lwr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

# Function to plot mixed effects model segmented regressions

This took a while to get running, but I think it works well now. I had to use base plot to get it to work. Note: x.variable and y.variable must be inputted as character strings.

I split the function into two so that we could customize the plots for LFM and MPa separately and also make the lines of code shorter and neater by involving more default values for arguments in the function

```{r}
rsegplot.lfm <- function(model, dataframe, species, x.variable = 'lfm', y.variable, max.x = max.lfm, x.lab = 'Live Fuel Moisture (%)', y.lab = NULL, tlp = NULL, tlp.upper = NULL, tlp.lower = NULL, color = 'color') {
  
p <- summary.segmented(model)$psi[2]
m <- slope(model, .coef = fixef(model))[[1]][[1]]
b <- intercept(model, .coef = fixef(model))[[1]][[1]]
m2 <- slope(model, .coef = fixef(model))[[1]][[2]]
b2 <- intercept(model, .coef = fixef(model))[[1]][[2]]
yvar <- dataframe[,y.variable]
xvar <- dataframe[,x.variable]
colr <- dataframe[,color]
confint <- confint.segmented(model, x.variable, .coef=fixef(model))
lower <- confint[2]
upper <- confint[3]
ymax <- max(yvar)
ymin <- min(yvar)

wacky <- plot(xvar, yvar, xlim = c(0, max.x), ylim = c(ymin-0.05*ymin, ymax+0.05*ymax), 
              xlab = x.lab, ylab = y.lab,
              pch = 16, col = alpha(colr, 0.8),
              cex.lab = 1.1)
polygon(x = c(lower, upper, upper, lower), y = c(ymax + 0.2*ymax, ymax +0.2*ymax, ymin - 30, ymin - 30), col = alpha('gray', 0.3), lty = 2)
abline(v = tlp, col = alpha('#00C368', 0.7), cex = 3)
polygon(x = c(tlp.lower, tlp.upper, tlp.upper, tlp.lower), y = c(ymax +0.2*ymax, ymax +0.2*ymax, ymin -30, ymin -30), col = alpha('#00C368', 0.3), border = alpha('#00C368', 0.6))
legend('topleft', legend=if(species == 'ADFA'){
  c("September 2020", "January 2018", "December 2016")
}
else if(species == 'CEME'){
  c("September 2020", "January 2020", "December 2019")
},
       col=if(species == "ADFA") {
         c("#c1121f","#FF7262","#A4A7DE")
         }
        else if(species == "CEME") {
        c("#c1121f","#64A400","#669BBC")
        }, pch = 16, cex=0.9)
for(z in 1:length(xvar)){
  if(z < p){
    segments(x0 = 0, x1 = p, y0 = b, y1 = m*((b2 - b)/(m - m2))+b, lwd = 3, col = "#9D0208")
  }else{
    segments(x0 = p, x1 = max.x, y0 = m2*((b - b2)/(m2 - m))+b2 , y1 = m2*max.x + b2, lwd = 3, col = "#9D0208")}}
return(wacky)
}
```

```{r}
rsegplot.mpa <- function(model, dataframe, species, x.variable = 'mpa', y.variable, max.x = max.mpa, x.lab = 'Water Potential (MPa)', y.lab = NULL, tlp = NULL, tlp.upper = NULL, tlp.lower = NULL, color = 'color') 
  {
p <- summary.segmented(model)$psi[2]
m <- slope(model, .coef = fixef(model))[[1]][[1]]
b <- intercept(model, .coef = fixef(model))[[1]][[1]]
m2 <- slope(model, .coef = fixef(model))[[1]][[2]]
b2 <- intercept(model, .coef = fixef(model))[[1]][[2]]
yvar <- dataframe[,y.variable]
xvar <- dataframe[,x.variable]
colr <- dataframe[,color]
confint <- confint.segmented(model, x.variable, .coef=fixef(model))
lower <- confint[2]
upper <- confint[3]
ymax <- max(yvar)
ymin <- min(yvar)

wacky <- plot(xvar, yvar, xlim = c(-10, 0), ylim = c(ymin-1, ymax+1), 
              xlab = x.lab, ylab = y.lab,
              pch = 16, col = colr, cex.lab = 1.1)
polygon(x = c(lower, upper, upper, lower), y = c(ymax +1.5, ymax +1.5, ymin -1.5, ymin -1.5), col = alpha('gray', 0.3), lty = 2)
abline(v = tlp, col = alpha('#00C368', 0.8), cex = 3)
polygon(x = c(tlp.lower, tlp.upper, tlp.upper, tlp.lower), y = c(ymax +1.5, ymax +1.5, ymin -1.5, ymin -1.5), col = alpha('#00C368', 0.3), border = alpha('#00C368', 0.7))
abline(a = b, b = m, lwd = 3, col = "#9D0208")
legend(-2, ymax+0.05*ymax, legend=if(species == 'ADFA'){
  c("September 2020", "January 2018", "December 2016")
}
else if(species == 'CEME'){
  c("September 2020", "January 2020", "December 2019")
},
       col=if(species == "ADFA") {
         c("#c1121f","#FF7262","#A4A7DE")
         }
        else if(species == "CEME") {
        c("#c1121f","#64A400","#669BBC")
        }, pch = 16, cex=0.8)
for(j in 1:length(xvar)){
  if(j < p){
    segments(x0 = -10, x1 = p, y0 = (-10*m) + b , y1 = m2*((b - b2)/(m2 - m))+b2, lwd = 3, col = "#9D0208")
  }
  else{
    segments(x0 = p, x1 = max.x, y0 = m2*((b - b2)/(m2 - m))+b2, y1 = b2, lwd = 3, col = "#9D0208")
  }
    }
return(wacky)
}
```

x0 = -10, x1 = p, y0 = (-10*m) + b , y1 = m2*((b - b2)/(m2 - m))+b2

#---------------------------------
# CEME
## LFM
Scaling LFM (to try it out)
```{r}
seg.ceme.subset <- seg.ceme.subset %>% 
  mutate(lfm.scaled = scale(lfm))
```

### PC1 (Scaled LFM)
```{r}
o.mod<-lme(PC1~lfm.scaled + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm.scaled, npsi=list(lfm.scaled=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', x.variable = "lfm.scaled", y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme, max.x = 3)
```

### PC1
```{r}
o.mod.a<-lme(PC1~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.a<-segmented.default(o.mod.a, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.a)

rsegplot.lfm(os.mod.a, seg.ceme.subset, 'CEME', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

#### Split by Sampling Date
```{r}
o.mod<-lme(PC1~lfm + site, random=~1|id, data=seg.ceme.s20.subset)
os.mod.a1<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.a1)

rsegplot.lfm(os.mod.a1, seg.ceme.s20.subset, 'CEME', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

```{r}
o.mod<-lme(PC1~lfm, random=~1|id, data=seg.ceme.d19.subset)
os.mod.a2<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.a2)

rsegplot.lfm(os.mod.a2, seg.ceme.d19.subset, 'CEME', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

### PC2
```{r}
o.mod<-lme(PC2~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'PC2',y.lab = "PC2", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```
 
Ignitability Metrics:
### Time to Ignition
```{r}
o.mod<-lme(tti~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.b<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.b)

u.mod <- lm(tti~lfm + year.month + site, data = seg.ceme.subset)
u.mod.b <- segmented(u.mod, ~lfm)
davies.test(u.mod.b)
summary.segmented(u.mod.b)

rsegplot.lfm(os.mod.b, seg.ceme.subset, 'CEME', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

#### Split by Sampling Date
```{r}
o.mod<-lme(tti~lfm + site, random=~1|id, data=seg.ceme.s20.subset)
os.mod.b1<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.b1)

rsegplot.lfm(os.mod.b1, seg.ceme.s20.subset, 'CEME', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

```{r}
o.mod<-lme(tti~lfm, random=~1|id, data=seg.ceme.d19.subset)
os.mod.b2<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.b2)

rsegplot.lfm(os.mod.b2, seg.ceme.d19.subset, 'CEME', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

### Prop. Ignite (5%)
```{r}
o.mod<-lme(prop.ignite.bins5_nodate~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'prop.ignite.bins5_nodate',y.lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

### Glow to Ignition
```{r}
o.mod<-lme(gti~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'gti',y.lab = "Glow to Ignition (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

Combustibility Metrics:
### Flame Height
```{r}
o.mod<-lme(fh~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

#### Split by Sampling Date
```{r}
o.mod<-lme(fh~lfm + site, random=~1|id, data=seg.ceme.s20.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.s20.subset, 'CEME', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

```{r}
o.mod<-lme(fh~lfm, random=~1|id, data=seg.ceme.d19.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.d19.subset, 'CEME', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

### Max. Temp.
```{r}
o.mod<-lme(temp.max~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'temp.max',y.lab = "Maximum Temperature (C)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

Sustainability Metrics:
### Flame Duration
```{r}
o.mod<-lme(fd~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.f<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.f)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'fd',y.lab = "Flame Duration (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

Consumability Metrics:
### Glow Duration
```{r}
o.mod<-lme(gd~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.h<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.h)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'gd',y.lab = "Glow Duration (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

### Post-Flame Glow
```{r}
o.mod<-lme(pfg~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'pfg',y.lab = "Post-Flame Glow (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```

### Time to First Glow
```{r}
o.mod<-lme(ttfg~lfm + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

confint.segmented(os.mod, 'lfm', .coef=fixef(os.mod))

rsegplot.lfm(os.mod, seg.ceme.subset, 'CEME', y.variable = 'ttfg',y.lab = "Time to First Glow (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
```
# -------
## Water Potential
```{r}
seg.ceme.subset <- seg.ceme.subset %>% 
  mutate(mpa.scaled = scale(mpa))
```

### PC1 (scaled)
```{r}
o.mod<-lme(PC1~mpa.scaled + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa.scaled, npsi=list(mpa.scaled=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME',x.variable = 'mpa.scaled', y.variable = 'PC1',y.lab = "PC1", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme, max.x = 4)
```

### PC1
```{r}
o.mod<-lme(PC1~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.a1<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.a1)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'PC1',y.lab = "PC1", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

### PC2
```{r}
o.mod<-lme(PC2~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'PC2',y.lab = "PC2", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```
 
Ignitability Metrics:
### Time to Ignition
```{r}
o.mod<-lme(tti~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.b1<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.b1)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

### Prop. Ignite (5%)
```{r}
o.mod<-lme(prop.ignite.bins5_nodate~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'prop.ignite.bins5_nodate',y.lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

### Glow to Ignition
```{r}
o.mod<-lme(gti~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'gti',y.lab = "Glow to Ignition (s)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

Combustibility Metrics:
### Flame Height
```{r}
o.mod<-lme(fh~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

#### Split by Sampling Date

```{r}
o.mod<-lme(fh~mpa + site, random=~1|id, data=seg.ceme.s20.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.s20.subset, 'CEME', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

```{r}
o.mod<-lme(fh~mpa, random=~1|id, data=seg.ceme.d19.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.d19.subset, 'CEME', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

### Max. Temp.
```{r}
o.mod<-lme(temp.max~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'temp.max',y.lab = "Maximum Temperature (C)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

Sustainability Metrics:
### Flame Duration
```{r}
o.mod<-lme(fd~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.f1<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.f1)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'fd',y.lab = "Flame Duration (s)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

Consumability Metrics:
### Glow Duration
```{r}
o.mod<-lme(gd~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod.h1<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.h1)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'gd',y.lab = "Glow Duration (s)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

### Post-Flame Glow
```{r}
o.mod<-lme(pfg~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'pfg',y.lab = "Post-Flame Glow (s)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

### Time to First Glow
```{r}
o.mod<-lme(ttfg~mpa + year.month + site, random=~1|id, data=seg.ceme.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.ceme.subset, 'CEME', y.variable = 'ttfg',y.lab = "Time to First Glow (s)", tlp = mean_mpa_ceme, tlp.lower = lwr_mpa_ceme, tlp.upper = upr_mpa_ceme)
```

#---------------------------------
# ADFA
## LFM
### PC1
```{r}
o.mod<-lme(PC1~ lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod.c<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.c)

rsegplot.lfm(os.mod.c, seg.adfa.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

#### Split by Sampling Date
```{r}
o.mod<-lme(PC1~ lfm + site, random=~1|id, data=seg.adfa.s20.subset)
os.mod.c1<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.c1)

rsegplot.lfm(os.mod.c1, seg.adfa.s20.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

```{r}
o.mod<-lme(PC1~ lfm, random=~1|id, data=seg.adfa.d16.subset)
os.mod.c2<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.c2)

rsegplot.lfm(os.mod.c1, seg.adfa.s20.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
rsegplot.lfm(os.mod.c2, seg.adfa.d16.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

### PC2
```{r}
o.mod<-lme(PC2~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'PC2',y.lab = "PC2", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```
 
Ignitability Metrics:
### Time to Ignition
```{r}
o.mod<-lme(tti~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod.d<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.d)

rsegplot.lfm(os.mod.d, seg.adfa.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

#### Split by Sampling Date
```{r}
o.mod<-lme(tti~lfm + site, random=~1|id, data=seg.adfa.s20.subset)
os.mod.d1<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.d1)

rsegplot.lfm(os.mod.d1, seg.adfa.s20.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

```{r}
o.mod<-lme(tti~lfm, random=~1|id, data=seg.adfa.d16.subset)
os.mod.d2<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.d2)

rsegplot.lfm(os.mod.d2, seg.adfa.d16.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

### Prop. Ignite (5%)
```{r}
o.mod<-lme(prop.ignite.bins5_nodate~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'prop.ignite.bins5_nodate',y.lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

### Glow to Ignition
```{r}
o.mod<-lme(gti~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'gti',y.lab = "Glow to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

Combustibility Metrics:
### Flame Height
```{r}
o.mod<-lme(fh~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

#### Split by Sampling Date
```{r}
o.mod<-lme(fh~lfm + site, random=~1|id, data=seg.adfa.s20.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.s20.subset, 'ADFA', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

```{r}
o.mod<-lme(fh~lfm, random=~1|id, data=seg.adfa.d16.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.d16.subset, 'ADFA', y.variable = 'fh',y.lab = "Flame Height (cm)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
```

### Max. Temp.
```{r}
o.mod<-lme(temp.max~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'temp.max',y.lab = "Maximum Temperature (C)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa)
```

Sustainability Metrics:
### Flame Duration
```{r}
o.mod<-lme(fd~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod.e<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.e)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'fd',y.lab = "Flame Duration (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa)
```

Consumability Metrics:
### Glow Duration
```{r}
o.mod<-lme(gd~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod.g<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.g)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'gd',y.lab = "Glow Duration (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa)
```

### Post-Flame Glow
```{r}
o.mod<-lme(pfg~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'pfg',y.lab = "Post-Flame Glow (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa)
```

### Time to First Glow
```{r}
o.mod<-lme(ttfg~lfm + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~lfm, npsi=list(lfm=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

confint.segmented(os.mod, 'lfm', .coef=fixef(os.mod))

rsegplot.lfm(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'ttfg',y.lab = "Time to First Glow (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa)
```

# ------
## Water Potential
### PC1
```{r}
o.mod<-lme(PC1~mpa + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod.c1<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.c1)

rsegplot.mpa(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

#### Split by Sampling Date
```{r}
o.mod<-lme(PC1~mpa + site, random=~1|id, data=seg.adfa.s20.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.adfa.s20.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

```{r}
o.mod<-lme(PC1~mpa, random=~1|id, data=seg.adfa.d16.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.adfa.d16.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

### PC2
```{r}
o.mod<-lme(PC2~mpa + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'PC2',y.lab = "PC2", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```
 
Ignitability Metrics:
### Time to Ignition
```{r}
o.mod<-lme(tti~mpa + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod.d1<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.d1)

rsegplot.mpa(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

### Prop. Ignite (5%)
```{r}
o.mod<-lme(prop.ignite.bins5_nodate~mpa + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'prop.ignite.bins5_nodate',y.lab = "Proportion Ignted (5% Bins of LFM)", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

### Glow to Ignition
```{r}
o.mod<-lme(gti~mpa + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

plot.segmented(os.mod, "mpa", .coef=fixef(os.mod), conf.level=.95)

rsegplot.mpa(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'gti',y.lab = "Glow to Ignition (s)", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

Combustibility Metrics:
### Flame Height
No threshold able to be identified (segmented.default returns error)

### Max. Temp.
No threshold able to be identified (segmented.default returns error)

Sustainability Metrics:
### Flame Duration
No threshold able to be identified (segmented.default returns error)

Consumability Metrics:
### Glow Duration
```{r}
o.mod<-lme(gd~mpa + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod.g1<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod.g1)

rsegplot.mpa(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'gd',y.lab = "Glow Duration (s)", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

### Post-Flame Glow
```{r}
o.mod<-lme(pfg~mpa + year.month + site, random=~1|id, data=seg.adfa.subset)
os.mod<-segmented.default(o.mod, ~mpa, npsi=list(mpa=1))
#summarizing results (note the '.coef' argument)
summary.segmented(os.mod)

rsegplot.mpa(os.mod, seg.adfa.subset, 'ADFA', y.variable = 'pfg',y.lab = "Post-Flame Glow (s)", tlp = mean_mpa_adfa, tlp.lower = lwr_mpa_adfa, tlp.upper = upr_mpa_adfa)
```

### Time to First Glow
No threshold able to be identified (segmented.default returns error)

# ---------------------------------
# Main Figure: Arranging Plots

Time to ignition plots
```{r}
rsegplot.lfm(os.mod.d, seg.adfa.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)

p <- summary.segmented(model)$psi[2]
m <- slope(model, .coef = fixef(model))[[1]][[1]]
b <- intercept(model, .coef = fixef(model))[[1]][[1]]
m2 <- slope(model, .coef = fixef(model))[[1]][[2]]
b2 <- intercept(model, .coef = fixef(model))[[1]][[2]]
yvar <- seg.adfa.subset[,'tti']
xvar <- dataframe[,x.variable]
colr <- dataframe[,color]
confint <- confint.segmented(model, x.variable, .coef=fixef(model))
lower <- confint[2]
upper <- confint[3]
ymax <- max(yvar)
ymax
ymin <- min(yvar)

plot(xvar, yvar, xlim = c(0, max.x), ylim = c(ymin-0.05*ymin, ymax+0.05*ymax), 
              xlab = x.lab, ylab = y.lab,
              pch = 16, col = alpha(colr, 0.8),
              cex.lab = 1.1)
polygon(x = c(lower, upper, upper, lower), y = c(ymax + 0.2*ymax, ymax +0.2*ymax, ymin - 30, ymin - 30), col = alpha('gray', 0.3), lty = 2)
abline(v = tlp, col = alpha('#00C368', 0.7), cex = 3)
polygon(x = c(tlp.lower, tlp.upper, tlp.upper, tlp.lower), y = c(ymax +0.2*ymax, ymax +0.2*ymax, ymin -30, ymin -30), col = alpha('#00C368', 0.3), border = alpha('#00C368', 0.6))
legend('topleft', legend=if(species == 'ADFA'){
  c("September 2020", "January 2018", "December 2016")
}
else if(species == 'CEME'){
  c("September 2020", "January 2020", "December 2019")
},
       col=if(species == "ADFA") {
         c("#c1121f","#FF7262","#A4A7DE")
         }
        else if(species == "CEME") {
        c("#c1121f","#64A400","#669BBC")
        }, pch = 16, cex=0.9)
for(z in 1:length(xvar)){
  if(z < p){
    segments(x0 = 0, x1 = p, y0 = b, y1 = m*((b2 - b)/(m - m2))+b, lwd = 3, col = "#9D0208")
  }else{
    segments(x0 = p, x1 = max.x, y0 = m2*((b - b2)/(m2 - m))+b2 , y1 = m2*max.x + b2, lwd = 3, col = "#9D0208")}}
```

```{r}
confint <- confint.segmented(os.mod.d, 'lfm', .coef=fixef(os.mod.d))
lower.d <- confint[2]
upper.d <- confint[3]

plot(seg.adfa.subset[,'lfm'], seg.adfa.subset[, 'tti'], xlim = c(0, max.lfm.a), ylim = c(-17, 75+0.05*75),
              xlab = 'Live Fuel Moisture (%)', ylab = 'Time to Ignition',
              pch = 16, col = alpha(seg.adfa.subset[,'color'], 0.8),
              cex.lab = 1.1)
polygon(x = c(lower.d, upper.d, upper.d, lower.d), y = c(75 + 0.2*75, 75 +0.2*75, -22, -22), col = alpha('gray', 0.3), lty = 2)
abline(v = mean_lfm_adfa, col = alpha('#00C368', 0.7), cex = 3)
polygon(x = c(lwr_lfm_adfa, upr_lfm_adfa, upr_lfm_adfa, lwr_lfm_adfa), y = c(75 +0.2*75, 75 +0.2*75, 0-22, -22), col = alpha('#00C368', 0.3), border = alpha('#00C368', 0.6))
legend('topleft', legend = c("September 2020", "January 2018", "December 2016"),
       col = c("#c1121f","#FF7262","#A4A7DE"), pch = 16, cex=0.9)
for(z in 1:length(seg.adfa.subset[,'lfm'])){
  if(z < summary.segmented(os.mod.d)$psi[2]){
    segments(x0 = 0, x1 = summary.segmented(os.mod.d)$psi[2], y0 = intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]], y1 = slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]]*((intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]] - intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]])/(slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]] - slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]]))+intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]], lwd = 3, col = "#9D0208")
  }else{
    segments(x0 = summary.segmented(os.mod.d)$psi[2], x1 = max.lfm, y0 = slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]]*((intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]] - intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]])/(slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]] - slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]]))+intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]] , y1 = slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]]*max.lfm + intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]], lwd = 3, col = "#9D0208")}}
draw.circle(43.1461, -10, 1.25, col = 'black') # Prop ignite threshold
segments(x0 = 39.0287, x1 = 47.2636, y0 = -10, y1 = -10, col = 'black')
text(x = 43.1461, y = -6.75, labels = c("Prop. Ignite (5% Bins)"), cex = 0.5)
draw.circle(98.2788, -15, 1.25, col = 'black') # Glow to ignition threshold
segments(x0 = 78.4386, x1 = 118.119, y0 = -15, y1 = -15, col = 'black')
text(x = 98.2788, y = -11.75, labels = c("Glow to Ignition"), cex = 0.5)
draw.circle(78.9439, 0, 1.25, col = 'black') # Flame height threshold
segments(x0 = 69.1201, x1 = 88.7678, y0 = 0, y1 = 0, col = 'black')
text(x = 78.9439, y = 3.25, labels = c("Flame Height"), cex = 0.5)
draw.circle(65.5869, -16.5, 1.25, col = 'black') # Post-flame glow threshold
segments(x0 = 51.3356, x1 = 79.8382, y0 = -16.5, y1 = -16.5, col = 'black')
text(x = 65.5869, y = -13.25, labels = c("Post-Flame Glow"), cex = 0.5)
draw.circle(46.453, 0, 1.25) # Flame duration threshold
segments(x0 = 32.1032, x1 = 60.8027, y0 = 0, y1 = 0, col = 'black')
text(x = 46.453, y = 3.25, labels = c("Flame Duration"), cex = 0.5)
draw.circle(98.2788, -3.5, 1.25, col = 'black') # Maximum temp. threshold
segments(x0 = 80.4224, x1 = 116.135, y0 = -3.5, y1 = -3.5, col = 'black')
text(x = 98.2788, y = -0.25, labels = c("Max. Temp."), cex = 0.5)
draw.circle(65.8129, -5, 1.25) # Glow duration threshold
segments(x0 = 48.3101, x1 = 83.3156, y0 = -5, y1 = -5, col = 'black')
text(x = 65.8129, y = -1.75, labels = c("Glow Duration"), cex = 0.5)
draw.circle(78.5259, -10, 1.25, col = 'black') # Time to first glow threshold
segments(x0 = 65.3508, x1 = 91.701, y0 = -10, y1 = -10, col = 'black')
text(x = 78.5259, y = -6.75, labels = c("Time to First Glow"), cex = 0.5)
```

```{r}
jpeg(here('figures', 'seg.reg.rand.plot.jpg'), width = 1200, height = 900, res = 100)
par(mfrow = c(2,2))
par(font.lab = 2)

rsegplot.lfm(os.mod.a, seg.ceme.subset, 'CEME', y.variable = 'PC1',y.lab = "Ignitability-Combustibility Proxy", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)
mtext("A", font = 2, cex = 2, side = 3, line = 1, at = 0)

#-----------------------------------------------------------------------

confint <- confint.segmented(os.mod.b, 'lfm', .coef=fixef(os.mod.b))
lower.b <- confint[2]
upper.b <- confint[3]

plot(seg.ceme.subset[,'lfm'], seg.ceme.subset[, 'tti'], xlim = c(0, max.lfm), ylim = c(-15, 86+0.05*86),
              xlab = 'Live Fuel Moisture (%)', ylab = 'Time to Ignition',
              pch = 16, col = alpha(seg.ceme.subset[,'color'], 0.8),
              cex.lab = 1.1)
polygon(x = c(lower.b, upper.b, upper.b, lower.b), y = c(86 + 0.2*86, 86 +0.2*86, -22, -22), col = alpha('gray', 0.3), lty = 2)
abline(v = mean_lfm_ceme, col = alpha('#00C368', 0.7), cex = 3)
polygon(x = c(lwr_lfm_ceme, upr_lfm_ceme, upr_lfm_ceme, lwr_lfm_ceme), y = c(86 +0.2*86, 86 +0.2*86, 0-22, -22), col = alpha('#00C368', 0.3), border = alpha('#00C368', 0.6))
legend('topleft', legend = c("September 2020", "January 2020", "December 2019"),
       col = c("#c1121f","#64A400","#669BBC"), pch = 16, cex=0.9)
for(z in 1:length(seg.ceme.subset[,'lfm'])){
  if(z < summary.segmented(os.mod.b)$psi[2]){
    segments(x0 = 0, x1 = summary.segmented(os.mod.b)$psi[2], y0 = intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[1]], y1 = slope(os.mod.b, .coef = fixef(os.mod.b))[[1]][[1]]*((intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]] - intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[1]])/(slope(os.mod.b, .coef = fixef(os.mod.b))[[1]][[1]] - slope(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]]))+intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[1]], lwd = 3, col = "#9D0208")
  }else{
    segments(x0 = summary.segmented(os.mod.b)$psi[2], x1 = max.lfm, y0 = slope(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]]*((intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[1]] - intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]])/(slope(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]] - slope(os.mod.b, .coef = fixef(os.mod.b))[[1]][[1]]))+intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]] , y1 = slope(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]]*max.lfm + intercept(os.mod.b, .coef = fixef(os.mod.b))[[1]][[2]], lwd = 3, col = "#9D0208")}}
draw.circle(91.053, -7, 2, col = 'black') # Prop ignite threshold
segments(x0 = 79.2544, x1 = 102.851, y0 = -7, y1 = -7, col = 'black')
text(x = 91.053, y = -4, labels = c("Prop. Ignite (5% Bins)"), cex = 0.5)
draw.circle(120.89, -15, 2, col = 'black') # Glow to ignition threshold
segments(x0 = 81.5424, x1 = 160.237, y0 = -15, y1 = -15, col = 'black')
text(x = 120.89, y = -12, labels = c("Glow to Ignition"), cex = 0.5)
draw.circle(57.0196, -7, 2, col = 'black') # Flame height threshold
segments(x0 = 47.4926, x1 = 66.5465, y0 = -7, y1 = -7, col = 'black')
text(x = 57.0196, y = -4, labels = c("Flame Height"), cex = 0.5)
draw.circle(68.003, -11.5, 2, col = 'black') # Post-flame glow threshold
segments(x0 = 49.5801, x1 = 86.4253, y0 = -11.5, y1 = -11.5, col = 'black')
text(x = 75.003, y = -8.5, labels = c("Post-Flame Glow"), cex = 0.5)
draw.circle(48.83, -16, 2) # Flame duration threshold
segments(x0 = 33.8529, x1 = 63.8074, y0 = -16, y1 = -16, col = 'black')
text(x = 48.83, y = -13, labels = c("Flame Duration"), cex = 0.5)
draw.circle(55.385, 0, 2) # Maximum temp. threshold
segments(x0 = 43.2009, x1 = 67.5694, y0 = 0, y1 = 0, col = 'black')
text(x = 53.385, y = 3, labels = c("Max. Temp."), cex = 0.5)
draw.circle(64.737, 5.5, 2) # Glow duration threshold
segments(x0 = 45.3899, x1 = 82.0848, y0 = 5.5, y1 = 5.5, col = 'black')
text(x = 64.737, y = 8.5, labels = c("Glow Duration"), cex = 0.5)
draw.circle(59.153, 12, 2) # Time to first glow threshold
segments(x0 = 43.6794, x1 = 74.626, y0 = 12, y1 = 12, col = 'black')
text(x = 59.153, y = 15, labels = c("Time to First Glow"), cex = 0.5)
mtext("B", font = 2, cex = 2, side = 3, line = 1, at = 0)

#-----------------------------------------------------------------------

rsegplot.lfm(os.mod.c, seg.adfa.subset, 'ADFA', y.variable = 'PC1',y.lab = "Ignitability-Combustibility Proxy", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)
mtext("C", font = 2, cex = 2, side = 3, line = 1, at = 0)

#-----------------------------------------------------------------------

confint <- confint.segmented(os.mod.d, 'lfm', .coef=fixef(os.mod.d))
lower.d <- confint[2]
upper.d <- confint[3]

plot(seg.adfa.subset[,'lfm'], seg.adfa.subset[, 'tti'], xlim = c(0, max.lfm.a), ylim = c(-17, 75+0.05*75),
              xlab = 'Live Fuel Moisture (%)', ylab = 'Time to Ignition',
              pch = 16, col = alpha(seg.adfa.subset[,'color'], 0.8),
              cex.lab = 1.1)
polygon(x = c(lower.d, upper.d, upper.d, lower.d), y = c(75 + 0.2*75, 75 +0.2*75, -22, -22), col = alpha('gray', 0.3), lty = 2)
abline(v = mean_lfm_adfa, col = alpha('#00C368', 0.7), cex = 3)
polygon(x = c(lwr_lfm_adfa, upr_lfm_adfa, upr_lfm_adfa, lwr_lfm_adfa), y = c(75 +0.2*75, 75 +0.2*75, 0-22, -22), col = alpha('#00C368', 0.3), border = alpha('#00C368', 0.6))
legend('topleft', legend = c("September 2020", "January 2018", "December 2016"),
       col = c("#c1121f","#FF7262","#A4A7DE"), pch = 16, cex=0.9)
for(z in 1:length(seg.adfa.subset[,'lfm'])){
  if(z < summary.segmented(os.mod.d)$psi[2]){
    segments(x0 = 0, x1 = summary.segmented(os.mod.d)$psi[2], y0 = intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]], y1 = slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]]*((intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]] - intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]])/(slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]] - slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]]))+intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]], lwd = 3, col = "#9D0208")
  }else{
    segments(x0 = summary.segmented(os.mod.d)$psi[2], x1 = max.lfm, y0 = slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]]*((intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]] - intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]])/(slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]] - slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[1]]))+intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]] , y1 = slope(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]]*max.lfm + intercept(os.mod.d, .coef = fixef(os.mod.d))[[1]][[2]], lwd = 3, col = "#9D0208")}}
draw.circle(43.1461, -10, 1.25, col = 'black') # Prop ignite threshold
segments(x0 = 39.0287, x1 = 47.2636, y0 = -10, y1 = -10, col = 'black')
text(x = 43.1461, y = -6.75, labels = c("Prop. Ignite (5% Bins)"), cex = 0.5)
draw.circle(98.2788, -15, 1.25, col = 'black') # Glow to ignition threshold
segments(x0 = 78.4386, x1 = 118.119, y0 = -15, y1 = -15, col = 'black')
text(x = 98.2788, y = -11.75, labels = c("Glow to Ignition"), cex = 0.5)
draw.circle(78.9439, 0, 1.25, col = 'black') # Flame height threshold
segments(x0 = 69.1201, x1 = 88.7678, y0 = 0, y1 = 0, col = 'black')
text(x = 78.9439, y = 3.25, labels = c("Flame Height"), cex = 0.5)
draw.circle(65.5869, -16.5, 1.25, col = 'black') # Post-flame glow threshold
segments(x0 = 51.3356, x1 = 79.8382, y0 = -16.5, y1 = -16.5, col = 'black')
text(x = 65.5869, y = -13.25, labels = c("Post-Flame Glow"), cex = 0.5)
draw.circle(46.453, 0, 1.25) # Flame duration threshold
segments(x0 = 32.1032, x1 = 60.8027, y0 = 0, y1 = 0, col = 'black')
text(x = 46.453, y = 3.25, labels = c("Flame Duration"), cex = 0.5)
draw.circle(98.2788, -3.5, 1.25, col = 'black') # Maximum temp. threshold
segments(x0 = 80.4224, x1 = 116.135, y0 = -3.5, y1 = -3.5, col = 'black')
text(x = 98.2788, y = -0.25, labels = c("Max. Temp."), cex = 0.5)
draw.circle(65.8129, -5, 1.25) # Glow duration threshold
segments(x0 = 48.3101, x1 = 83.3156, y0 = -5, y1 = -5, col = 'black')
text(x = 65.8129, y = -1.75, labels = c("Glow Duration"), cex = 0.5)
draw.circle(78.5259, -10, 1.25, col = 'black') # Time to first glow threshold
segments(x0 = 65.3508, x1 = 91.701, y0 = -10, y1 = -10, col = 'black')
text(x = 78.5259, y = -6.75, labels = c("Time to First Glow"), cex = 0.5)
mtext("D", font = 2, cex = 2, side = 3, line = 1, at = 0)

dev.off()
```

# ---------------------------------
# Splitting by Sampling Date
```{r}
jpeg(here('figures', 'seg.reg.rand.sDATES.jpg'), width = 1500, height = 2000, res = 150)
par(mfrow = c(4,3))
par(font.lab = 2)

rsegplot.lfm(os.mod.a, seg.ceme.subset, 'CEME', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)

rsegplot.lfm(os.mod.a1, seg.ceme.s20.subset, 'CEME', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)

rsegplot.lfm(os.mod.a2, seg.ceme.d19.subset, 'CEME', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)

rsegplot.lfm(os.mod.b, seg.ceme.subset, 'CEME', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)

rsegplot.lfm(os.mod.b1, seg.ceme.s20.subset, 'CEME', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)

rsegplot.lfm(os.mod.b2, seg.ceme.d19.subset, 'CEME', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_ceme, tlp.lower = lwr_lfm_ceme, tlp.upper = upr_lfm_ceme)

rsegplot.lfm(os.mod.c, seg.adfa.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)

rsegplot.lfm(os.mod.c1, seg.adfa.s20.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)

rsegplot.lfm(os.mod.c2, seg.adfa.d16.subset, 'ADFA', y.variable = 'PC1',y.lab = "PC1", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)

rsegplot.lfm(os.mod.d, seg.adfa.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)

rsegplot.lfm(os.mod.d1, seg.adfa.s20.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)

rsegplot.lfm(os.mod.d2, seg.adfa.d16.subset, 'ADFA', y.variable = 'tti',y.lab = "Time to Ignition (s)", tlp = mean_lfm_adfa, tlp.lower = lwr_lfm_adfa, tlp.upper = upr_lfm_adfa, max.x = max.lfm.a)

dev.off()
```