---
title: "Segmented Regressions - Linear Models"
author: "Indra Boving & Joe Celebrezze"
date: "6/7/2022"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
library(lubridate)
library(MetBrewer)
library(lattice)
library(gt)
library(gtsummary)
filter = dplyr::filter 
rename = dplyr::rename
here = here::here
```

# Reading in Dataframes
Using all dates instead of just Sept. 2020 data
```{r}
seg.data.subset <- read.csv(here('processed-data', 'seg.reg.data.local.csv'))

seg.data.subset.alldates <- read.csv(here('processed-data', 'mem.data.subset.alldates'))

scaled.mem.data.alldates <- read.csv(here('processed-data', 'mem.data.local.epi.alldates.csv'))
```

# Data Wrangling
For the segmented regressions, we debated using seasonal LFM minimums and maximums to limit the dataset, but instead -- since we wanted to keep the datasets similar for each analysis -- we used the dataset that was used in the mixed effects model analysis

## Species Split
```{r}
seg.adfa.subset <- seg.data.subset %>% 
  filter(spp == "ADFA")

seg.ceme.subset <- seg.data.subset %>% 
  filter(spp == "CEME")
```

## PV Data, TLP
Getting PV data, TLP stuff all ready for segmented regression visualizations (comparing breakpoint in segmented regression to turgor loss point derived from pressure-volume curves)

```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"))

pv_local <- pv_summary_df_timing %>% 
  filter(spp %in% c("ADFA", "CEME"))
```

```{r}
mean_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()

upr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()

lwr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()

mean_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()

upr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr)) %>% 
  pull()

lwr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

```{r}
mean_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()

upr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()

lwr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()

mean_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()

upr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr)) %>% 
  pull()

lwr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

```{r}
scaled.mem.data.alldates.noNAs <- scaled.mem.data.alldates %>% 
  drop_na(mpa, lfm, PC1)

tmp <- scaled.mem.data.alldates.noNAs %>% 
  mutate(tlp = case_when(
    spp == "ADFA" ~ mean_mpa_adfa, 
    spp == "CEME" ~ mean_mpa_ceme
  )) %>% 
  mutate(tlp_split = case_when(
    mpa > tlp ~ "tlp_above", 
    mpa < tlp ~ "tlp_below"
  )) 
tmp
```

# Global Options: Colors, Themes
```{r}
th <- theme(panel.background = element_rect(fill='white', colour='black'), # Make background white and border black
          panel.grid.major = element_blank(),  # Hide major gridlines
          panel.grid.minor = element_blank())

th.spp.wrap <- theme(legend.position = "bottom", 
        strip.text = element_text(face = "italic", size = 12) +
  scale_color_manual(values=met.brewer("Morgenstern", 7)))

Morgenstern = list(c("#7c668c", "#b08ba5", "#dfbbc8", "#ffc680", "#ffb178", "#db8872", "#a56457"), c(7, 5, 4, 6, 3, 2, 1), colorblind=TRUE)
```


# Functions

```{r, eval=F}
seg.setup <- function(x, y, df) {
  #out.lm<-lm({{y}}~{{x}}, data = data
  x <- enquo(x)
  y <- enquo(y)
  
#out.lm<-lm(paste(y, "~", x), data = df)

out.lm<-lm(y ~ x, data = df)

segmented.mod <- segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod) #CI of breakpoints
confint

lower <- confint[2] #lower bound
lower

upper <- confint[3] #upper bound
upper

fit <- numeric(length(df$x)) * NA

fit[complete.cases(rowSums(cbind(y, x)))] <- broken.line(segmented.mod)$fit

}

#seg.setup(lfm, PC1, seg.ceme.subset)
```

```{r}
segplot <- function(data, x, y, z, tlp_value, lwr, upr, lwr_seg, upr_seg) {
  ggplot(data, aes({{x}}, {{y}})) +
  geom_point()+
  geom_line(aes({{x}}, {{z}}), #segmented line
            color = "blue2") +
  geom_vline(xintercept = tlp_value, #tlp value line
             color = "gold1") +
  geom_ribbon(aes(xmin=lwr, xmax=upr), #tlp CI ribbon
              alpha = .3,
              color = "gold1") +
  geom_vline(xintercept = lwr_seg, #segmented CI line lower
             color = "blue2")+
  geom_vline(xintercept = upr_seg, #segmented CI line upper
             color = "blue2") +
  geom_ribbon(aes(xmin=lwr_seg, xmax=upr_seg), #segmented ribbon
              alpha = .3, 
              color = "blue2") +
   th #theme!
}
```
# ----------------------------------
# Start of Segmented Regressions
# ----------------------------------

# - Live Fuel Moisture -
# PC1

#### ADFA
```{r}
seg.adfa.subset <- seg.adfa.subset %>% 
  filter(lfm < 150)

out.lm<-lm(PC1 ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# Result: significant (p = 0.02517)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$PC1, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, PC1, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

#### CEME

```{r}
seg.ceme.subset <- seg.ceme.subset %>% 
  filter(lfm < 300)

out.lm<-lm(PC1 ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# Result: marginally significant (p = 0.04844)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$PC1, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, PC1, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```
 


```{r}
out.lm<-lm(PC1 ~ mpa, data = seg.adfa.subset.limited)
davies.test(out.lm, k = 50)
#Result: insignificant (p = 0.5455)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.limited$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.limited$PC1, seg.adfa.subset.limited$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.limited, mpa, PC1, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)

```
 
```{r}
out.lm<-lm(PC1 ~ mpa, data = seg.ceme.subset.limited)
davies.test(out.lm, k = 50)
#Result: P = 1?!

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.limited$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.limited$PC1, seg.ceme.subset.limited$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.limited, mpa, PC1, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```
# PC2

#### ADFA
```{r}
out.lm<-lm(PC2 ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# Result: insignificant (p = 0.178)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$PC1, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, PC2, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

#### CEME

```{r}
out.lm<-lm(PC2 ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# Result: significant (p = 0.01212)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$PC1, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, PC2, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# PC3

#### ADFA
```{r}
out.lm<-lm(PC3 ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# Result: significant (p = 0.0303)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$PC1, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, PC3, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

#### CEME
```{r}
out.lm<-lm(PC3 ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# Result: significant (p = 0.01461)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$PC1, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, PC3, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# Prop. Ignited (10% Bins)
## ADFA
```{r}
out.lm<-lm(prop.ignite.bins10_nodate ~ lfm, data = seg.adfa.subset) 
davies.test(out.lm, k = 50)
# Highly significant (p < 0.00005)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint(segmented.mod)

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$prop.ignite.bins5_nodate, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

segplot(seg.adfa.subset, lfm, prop.ignite.bins5_nodate, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

## CEME
```{r}
out.lm<-lm(prop.ignite.bins10_nodate ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: marginally significant (p = 0.04587)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$prop.ignite.bins10_nodate, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, prop.ignite.bins10_nodate, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# TTI

### ADFA
```{r}
out.lm<-lm(tti ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
#Result: significant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$tti, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit


segplot(seg.adfa.subset, lfm, tti, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
 
```
### CEME

```{r}
out.lm<-lm(tti ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# Result: highly significant (p = 0.0009369)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$tti, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, tti, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```



----
# FD

### ADFA

```{r}
#https://stats.stackexchange.com/questions/19772/estimating-the-break-point-in-a-broken-stick-piecewise-linear-model-with-rando/19777#19777

out.lm<-lm(fd ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k=50)
#Result: insignificant (p = 0.6856)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$fd, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, fd, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

### CEME
```{r}
out.lm<-lm(fd ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: insignificant (p = 0.4814)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$fd, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, fd, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# FH

### ADFA

```{r}
out.lm<-lm(fh ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# result: significant (p = 0.001313)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$fh, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, fh, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
out.lm<-lm(fh ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: significant (p = 0.03032)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$fh, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, fh, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# GD

### ADFA
```{r}
out.lm<-lm(gd ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$gd, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, gd, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
seg.ceme.subset.gd <- seg.ceme.subset %>% 
  filter(gd < 360) #Removing unrealistic glow durations
```


```{r}
out.lm <- lm(gd ~ lfm, data = seg.ceme.subset.gd)
davies.test(out.lm, k = 50)
#Result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.gd$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.gd$gd, seg.ceme.subset.gd$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.gd, lfm, gd, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```



```{r}
out.lm<-lm(gd ~ mpa, data = seg.ceme.subset.limited)
davies.test(out.lm, k = 50)
# Result: insignificant (p = 0.7217)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.limited$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.limited$gd, seg.ceme.subset.limited$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.limited, mpa, gd, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# GTI
No significant thresholds identified
### ADFA
```{r}
out.lm<-lm(gti ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$gti, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, gti, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
out.lm <- lm(gti ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$gti, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, gti, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# PFG
No significant thresholds identified
### ADFA
```{r}
out.lm<-lm(pfg ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$pfg, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, pfg, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
out.lm <- lm(pfg ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: marginally insignificant (p = 0.0667)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$pfg, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, pfg, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```



# Max. Temp.
### ADFA
```{r}
out.lm<-lm(temp.max ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$temp.max, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, temp.max, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

### CEME
```{r}
out.lm <- lm(temp.max ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: significant (p = 0.000395)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$temp.max, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, temp.max, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# TTFG

### ADFA
For time to first glow, there is one strange value remaining where it probably didn't glow or didn't ignite (ttfg = 490)
```{r}
seg.adfa.subset.ttfg <- seg.adfa.subset %>% 
  filter(ttfg < 300)
```

```{r}
out.lm<-lm(ttfg ~ lfm, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$ttfg, seg.adfa.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, lfm, ttfg, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

### CEME
```{r}
out.lm <- lm(ttfg ~ lfm, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: significant (p = 0.005595)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$ttfg, seg.ceme.subset$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, lfm, ttfg, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```
# -----------------------------------
# - Water Potential - 
# PC1
#### ADFA 
no breakpoint
```{r}
out.lm<-lm(PC1 ~ mpa, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
#Result: insignifcant (p = 0.6182)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

#fit[complete.cases(rowSums(cbind(seg.adfa.subset$PC1, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, mpa, PC1, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)
```
#### CEME
```{r}
out.lm<-lm(PC1 ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: insignificant (p = 0.6775)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
#segmented.mod
#summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$PC1, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, PC1, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# PC2

#### ADFA
```{r}
out.lm<-lm(PC2 ~ mpa, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# Result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$PC1, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, mpa, PC2, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)
```

#### CEME

```{r}
out.lm<-lm(PC2 ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# Result: insignificant (p = 0.3722)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$PC1, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, PC2, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# PC3

#### ADFA
```{r}
out.lm<-lm(PC3 ~ mpa, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# Result: insignificant (p = 1)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$PC1, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, mpa, PC3, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)
```

#### CEME
```{r}
out.lm<-lm(PC3 ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# Result: significant (p = 0.0311)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$PC1, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, PC3, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# Prop. Ignited (10% Bins)
## ADFA
```{r}
out.lm<-lm(prop.ignite.bins10_nodate ~ mpa, data = seg.adfa.subset) 
davies.test(out.lm, k = 50)
# insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint(segmented.mod)

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$prop.ignite.bins5_nodate, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

segplot(seg.adfa.subset, mpa, prop.ignite.bins5_nodate, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

## CEME
```{r}
out.lm<-lm(prop.ignite.bins10_nodate ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: insignificant (p = 1)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$prop.ignite.bins10_nodate, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, prop.ignite.bins10_nodate, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# TTI
#### ADFA
```{r}
out.lm<-lm(tti ~ mpa, data = seg.adfa.subset)
davies.test(out.lm, k=50)
# Result: insignificant (p = 0.6741)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$tti, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, mpa, tti, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)
```

#### CEME
```{r}
out.lm<-lm(tti ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: significant (p = 0.01178)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$tti, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, tti, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# FD
### ADFA
```{r}
out.lm<-lm(fd ~ mpa, data = seg.adfa.subset)
davies.test(out.lm, k=50)
# Result: insignificant (p = 0.7258)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$fd, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, mpa, fd, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)
```

### CEME
```{r}
out.lm<-lm(fd ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
#Result: insignificant (p = 0.7735)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$fd, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, fd, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# FH
#### ADFA
```{r}
out.lm<-lm(fh ~ mpa, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# Result: p = 1?!

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$fh, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, mpa, fh, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)
```

#### CEME
```{r}
out.lm<-lm(fh ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# result: significant (p = 0.001903)

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$fh, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, fh, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# GD
#### ADFA
```{r}
out.lm<-lm(gd ~ mpa, data = seg.adfa.subset)
davies.test(out.lm, k = 50)
# Result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset$gd, seg.adfa.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset, mpa, gd, fit, mean_mpa_adfa, lwr_mpa_adfa, upr_mpa_adfa, lower, upper)
```

#### CEME
```{r}
out.lm<-lm(gd ~ mpa, data = seg.ceme.subset)
davies.test(out.lm, k = 50)
# result: insignificant

#the simplest example: the starting model includes just 1 covariate
#.. and 1 breakpoint has to be estimated for that
segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset$mpa)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset$gd, seg.ceme.subset$mpa)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset, mpa, gd, fit, mean_mpa_ceme, lwr_mpa_ceme, upr_mpa_ceme, lower, upper)
```

# GTI

# PFG

# Max. Temp.

# TTFG


#-----------------------------------
# Visualizing distribution of identified thresholds

Making dataframe
```{r}
lfm.thresholds <- c(109.32, NA, 131.08, 71.523, 83.981, 85.741, 30.825, 98.265, 30.825, 96.118, NA, 84.143, 79.555, NA, 119.38, NA, NA, NA, NA, NA, 79.555, NA, 56.968, 74.711, NA, 106.85, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 65.876, NA, NA, NA, 103.01, NA)

spp.thresholds <- c("ADFA", "ADFA (limited)", "CEME", "CEME (limited)", "ADFA", "ADFA (limited)", "CEME", "CEME (limited)", "ADFA", "ADFA (limited)", "CEME", "CEME (limited)", "ADFA", "ADFA (limited)", "CEME", "CEME (limited)",  "ADFA", "ADFA (limited)", "CEME", "CEME (limited)","ADFA", "ADFA (limited)", "CEME", "CEME (limited)",  "ADFA", "ADFA (limited)", "CEME", "CEME (limited)", "ADFA", "ADFA (limited)", "CEME", "CEME (limited)", "ADFA", "ADFA (limited)", "CEME", "CEME (limited)", "ADFA", "ADFA (limited)", "CEME", "CEME (limited)", "ADFA", "ADFA (limited)", "CEME", "CEME (limited)")

metrics.thresholds <- c(rep("PC1", 4), rep("prop.ignite.10", 4), rep("prop.ignite.5", 4), rep("TTI", 4), rep("FD", 4), rep("FH", 4), rep("GD", 4), rep("GTI", 4), rep("PFG", 4), rep("temp.max", 4), rep("TTFG", 4))

threshold.df <- data.frame(lfm.thresholds, spp.thresholds, metrics.thresholds)

threshold.df <- threshold.df %>% 
  rename(threshold=lfm.thresholds) %>% 
  rename(species = spp.thresholds) %>%  
  rename(metric = metrics.thresholds)
```

```{r}
threshold.df %>% 
  na.omit() %>% 
  ggplot(aes(x = metric, y = threshold)) +
    geom_boxplot() +
    annotate("text", x = 1, y = 140, label = "n = 3") +
    annotate("text", x = 2, y = 140, label = "n = 1") +
    annotate("text", x = 3, y = 140, label = "n = 3") +
    annotate("text", x = 4, y = 140, label = "n = 4") +
    annotate("text", x = 5, y = 140, label = "n = 3") +
    annotate("text", x = 6, y = 140, label = "n = 1") +
    annotate("text", x = 7, y = 140, label = "n = 1") +
    annotate("text", x = 8, y = 140, label = "n = 2") +
    labs(x = "Metric", y = "Threshold (LFM)") +
    th

summary(threshold.df)

threshold.df %>% 
  filter(species == "CEME" | species == "CEME (limited)") %>% 
  filter(metric == "prop.ignite.10" | metric == "prop.ignite.5" | metric == "TTI" | metric == "PC1") %>% 
  summary()
```

