---
title: "Segmented Regressions: Bootstrapping Prior to Analysis"
author: "Indra Boving & Joe Celebrezze"
date: "7/21/2022"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
library(lubridate)
library(MetBrewer)
library(lattice)
library(gt)
library(gtsummary)
filter = dplyr::filter 
rename = dplyr::rename
here = here::here
group_by = dplyr::group_by
```

# Reading in Dataframes
Using all dates instead of just Sept. 2020 data
```{r}
seg.data.subset <- read.csv(here('processed-data', 'seg.reg.data.local.csv'))

seg.data.subset.alldates <- read.csv(here('processed-data', 'mem.data.subset.alldates'))
```

# Data Wrangling
For the segmented regressions, we debated using seasonal LFM minimums and maximums to limit the dataset, but instead -- since we wanted to keep the datasets similar for each analysis -- we used the dataset that was used in the mixed effects model analysis

## Species Split
```{r}
seg.adfa.subset <- seg.data.subset %>% 
  filter(spp == "ADFA") %>% 
  group_by(lfm.bin = cut(lfm, breaks= seq(0, 120, by = 6))) %>%  #Fixing the bins
  drop_na(PC1, lfm, year.month, site, id) %>% 
  select(PC1, PC2, tti, fh, temp.max, gd, gti, pfg, ttfg, fd, prop.ignite.bins5_nodate, lfm, lfm.bin, mpa, year.month, site, id)

seg.ceme.subset <- seg.data.subset %>% 
  filter(spp == "CEME") %>% 
  filter(lfm < 220) %>% 
  group_by(lfm.bin = cut(lfm, breaks= seq(0, 216, by = 12))) %>%  #Fixing the bins
  drop_na(PC1, lfm, year.month, site, id) %>% 
  select(PC1, PC2, tti, fh, temp.max, gd, gti, pfg, ttfg, fd, prop.ignite.bins5_nodate, lfm, lfm.bin, mpa, year.month, site, id)
```

# CEME

# 1. Pick the median bin density
```{r}
ceme.bin.n <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  count()

median(ceme.bin.n$n) # Median: 8
```

# 2. Resampling points from each bin
```{r}
ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)
```

# 3. Segmented Regression
```{r}
out.lm<-lm(PC2 ~ lfm + site + year.month, data = ceme.binned.df)
davies.test(out.lm, ~lfm, k = 50)

segmented.mod <- segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
summary(segmented.mod)
```

# 4. Iterating Above Process 100 Times
Holding vectors
```{r}
psi.PC1 <- c(rep(NaN, 100))
psi.PC2 <- c(rep(NaN, 100))
psi.tti <- c(rep(NaN, 100))
psi.fh <- c(rep(NaN, 100))
psi.fd <- c(rep(NaN, 100))
psi.gd <- c(rep(NaN, 100))
psi.gti <- c(rep(NaN, 100))
psi.pfg <- c(rep(NaN, 100))
psi.ttfg <- c(rep(NaN, 100))
psi.temp.max <- c(rep(NaN, 100))
psi.prop.ignite <- c(rep(NaN, 100))
ceme.thresholds <- data.frame(psi.PC1, psi.PC2, psi.tti, psi.fh, psi.temp.max, psi.gd, psi.gti, psi.pfg, psi.ttfg, psi.prop.ignite, psi.fd)
```

For loop
It is a bit clunky, but seems to do the trick. Could not figure out how to iterate dependent variables in the linear models.

Note: I did not include flame duration, glow-to-ignition or flame height below, as those variables were interrupting the for loop when they did not return a threshold
```{r}
for(i in 1:10){
   for(j in 1:nrow(ceme.thresholds)){
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)
  if(i == 1){
    out.lm<-lm(PC1 ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 2) {
  out.lm<-lm(PC2 ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 3) {
    out.lm<-lm(tti ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 5) {
    out.lm<-lm(temp.max ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 6) {
    out.lm<-lm(gd ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 8) {
    out.lm<-lm(pfg ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 9) {
    out.lm<-lm(ttfg ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 10) {
    out.lm<-lm(prop.ignite.bins5_nodate ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
   }}
```

Since the above for loop kept getting interrupted when thresholds were not discovered, I set up a new for loop to figure out which seeds are causing the interruptions and manually removing those seeds. For CEME, I did this for flame height, glow to ignition and flame duration

Flame Height:
```{r}
for(j in 1:nrow(ceme.thresholds)){
    set.seed(seed = j, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)

  out.lm<-lm(fh ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.fh[j] <- summary(segmented.mod)$psi[2]}
```
Huh.. Luckily, seeds 1:100 did not cause the for loop to be interrupted!

Glow to Ignition:
```{r}
for(j in 1:25){
  set.seed(seed = j, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)
  
 out.lm<-lm(gti ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}

for(j in 26:48){
  set.seed(seed = j+1, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)
  
 out.lm<-lm(gti ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}

for(j in 49:69){
  set.seed(seed = j+2, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)
  
 out.lm<-lm(gti ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}

for(j in 70:93){
  set.seed(seed = j+4, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)
  
 out.lm<-lm(gti ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}

for(j in 94:100){
  set.seed(seed = j+5, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)
  
 out.lm<-lm(gti ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}
```

Flame Duration:
```{r}
for(j in 1:68){
    set.seed(seed = j, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)

  out.lm<-lm(fd ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.fd[j] <- summary(segmented.mod)$psi[2]}

for(j in 69:100){
    set.seed(seed = j+1, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  ceme.binned.df <- seg.ceme.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(8, replace = T)

  out.lm<-lm(fd ~ lfm + site + year.month, data = ceme.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  ceme.thresholds$psi.fd[j] <- summary(segmented.mod)$psi[2]}
```


# 5. Mean Threshold Values
```{r}
summary(ceme.thresholds)
```

#-------------------------------

# ADFA

# 1. Pick the median bin density
```{r}
adfa.bin.n <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  count()

median(adfa.bin.n$n) # Median: 18.5; round to 19
```

# 2. Resampling points from each bin
```{r}
adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)
```

# 3. Segmented Regression
```{r}
out.lm<-lm(PC1 ~ lfm + site + year.month, data = adfa.binned.df)
davies.test(out.lm, ~lfm, k = 50)

segmented.mod <- segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
summary(segmented.mod)
```

# 4. Iterating Above Process 1000 Times
Holding vectors
```{r}
psi.PC1 <- c(rep(NaN, 100))
psi.PC2 <- c(rep(NaN, 100))
psi.tti <- c(rep(NaN, 100))
psi.fh <- c(rep(NaN, 100))
psi.fd <- c(rep(NaN, 100))
psi.gd <- c(rep(NaN, 100))
psi.gti <- c(rep(NaN, 100))
psi.pfg <- c(rep(NaN, 100))
psi.ttfg <- c(rep(NaN, 100))
psi.fd <- c(rep(NaN, 100))
psi.prop.ignite <- c(rep(NaN, 100))
psi.temp.max <- c(rep(NaN, 100))
adfa.thresholds <- data.frame(psi.PC1, psi.PC2, psi.tti, psi.fh, psi.fd, psi.gd, psi.gti, psi.pfg, psi.ttfg, psi.prop.ignite, psi.temp.max)
```

For loop
It is a bit clunky, but seems to do the trick. Could not figure out how to iterate dependent variables in the linear models.

```{r}
for(i in 1:10){
   for(j in 1:nrow(adfa.thresholds)){
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)
  if(i == 1){
    out.lm<-lm(PC1 ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 2) {
  out.lm<-lm(PC2 ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 3) {
    out.lm<-lm(tti ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 4) {
    out.lm<-lm(fh ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 5) {
    out.lm<-lm(fd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 8) {
    out.lm<-lm(pfg ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
  else if(i == 9) {
    out.lm<-lm(ttfg ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds[j,i] <- summary(segmented.mod)$psi[2]
  }
   }}
```

Since the above for loop kept getting interrupted when thresholds were not discovered, I set up a new for loop to figure out which seeds are causing the interruptions and manually removing those seeds. For ADFA, I did this for glow duration, glow to ignition, proportion ignited, and max. temp.

Glow Duration:
```{r}
for(j in 1:8){
  set.seed(seed = j, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 9:17){
  set.seed(seed = j+3, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 18:24){
  set.seed(seed = j+9, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 25:29){
  set.seed(seed = j+11, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 30:33){
  set.seed(seed = j+15, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 34:37){
  set.seed(seed = j+16, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 38:42){
  set.seed(seed = j+17, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 43:50){
  set.seed(seed = j+46, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 51:60){
  set.seed(seed = j+64, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 60:68){
  set.seed(seed = j+68, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 69:81){
  set.seed(seed = j+83, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 82:87){
  set.seed(seed = j+89, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 88:95){
  set.seed(seed = j+96, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}

for(j in 95:100){
  set.seed(seed = j+98, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gd ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gd[j] <- summary(segmented.mod)$psi[2]}
```
Oh boy that took a while.

Glow to Ignition:
```{r}
for(j in 1:28){
  set.seed(seed = j, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gti ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}

for(j in 29:77){
  set.seed(seed = j+10, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gti ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}

for(j in 78:100){
  set.seed(seed = j+50, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(gti ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.gti[j] <- summary(segmented.mod)$psi[2]}
```

Proportion Ignition:
No breakpoints estimated!

Maximum Temp.:
```{r}
for(j in 1:6){
  set.seed(seed = j, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}

for(j in 7:29){
  set.seed(seed = j+9, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}

for(j in 30:38){
  set.seed(seed = j+12, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}

for(j in 39:47){
  set.seed(seed = j+19, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}

for(j in 48:64){
  set.seed(seed = j+21, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}

for(j in 65:77){
  set.seed(seed = j+29, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}

for(j in 78:91){
  set.seed(seed = j+33, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}

for(j in 91:100){
  set.seed(seed = j+78, kind = 'default', normal.kind = 'default', sample.kind = 'default')
  
  adfa.binned.df <- seg.adfa.subset %>% 
  group_by(lfm.bin) %>% 
  sample_n(19, replace = T)

  out.lm<-lm(temp.max ~ lfm + site + year.month, data = adfa.binned.df)
  segmented.mod <- segmented(out.lm, seg.Z = ~lfm)
  adfa.thresholds$psi.temp.max[j] <- summary(segmented.mod)$psi[2]}
```

# 5. Mean Threshold Values
```{r}
summary(adfa.thresholds)
```
