---
title: 'Segmented Regressions (With Mixed Efffects Models): Percentile Ranks'
author: "Indra Boving & Joe Celebrezze"
date: "7/13/2022"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(tidyverse)
library(lme4)
library(here)
library(segmented)
library(nlme)
library(lubridate)
library(MetBrewer)
library(lattice)
library(gt)
library(gtsummary)
filter = dplyr::filter 
rename = dplyr::rename
here = here::here
group_by = dplyr::group_by
summarise = dplyr::summarise
```

# Reading in Dataframes
Using all dates instead of just Sept. 2020 data
```{r}
seg.data.subset <- read.csv(here('processed-data', 'seg.reg.data.local.csv'))

seg.data.subset.alldates <- read.csv(here('processed-data', 'mem.data.subset.alldates'))

scaled.mem.data.alldates <- read.csv(here('processed-data', 'mem.data.local.epi.alldates.csv'))

seg.data.subset <- seg.data.subset %>% 
  na.omit
```

# Data Wrangling
For the segmented regressions, we debated using seasonal LFM minimums and maximums to limit the dataset, but instead -- since we wanted to keep the datasets similar for each analysis -- we used the dataset that was used in the mixed effects model analysis

## Species Split
```{r}
seg.adfa.subset <- seg.data.subset %>% 
  filter(spp == "ADFA")

seg.ceme.subset <- seg.data.subset %>% 
  filter(spp == "CEME")
```

## Percentile Bins: Max's Suggestions
```{r}
seg.ceme.subset.p <- seg.ceme.subset %>% 
  group_by(gr) %>% 
  summarise(PC1 = mean(PC1), PC2 = mean(PC2), tti = mean(tti), prop.ignite.bins10_nodate = mean(prop.ignite.bins10_nodate), gti = mean(gti), fh = mean(fh), temp.max = mean(temp.max), fd = mean(fd), gd = mean(gd), pfg = mean(pfg), ttfg = mean(ttfg), lfm = mean(lfm))

#seg.ceme.subset.p <- seg.ceme.subset.p %>% 
  #filter(id == '2020_September_EPI_CEME_(100,110]_1.6'| id == '2020_September_EPI_CEME_(110,120]_2.3'| id == '2019_December_EPI_CEME_(120,130]_8'| id == '2019_December_EPI_CEME_(130,140]_4'| id == 	'2019_December_EPI_CEME_(140,150]_4'| id == '2020_September_EPI_CEME_(150,160]_2.3'| id == '2019_December_EPI_CEME_(160,170]_5'| id == '2019_December_EPI_CEME_(170,180]_2'| id == '2020_January_EPI_CEME_(180,190]_3' | id == '2019_December_EPI_CEME_(190,200]_8' | id == '2020_September_EPI_CEME_(20,30]_1.6' | id == '2020_January_EPI_CEME_(200,210]_1' | id == '2019_December_EPI_CEME_(220,230]_8' | id == '2020_January_EPI_CEME_(230,240]_5' | id == '2020_January_EPI_CEME_(240,250]_2' | id == '2019_December_EPI_CEME_(270,280]_1' | id == '2020_January_EPI_CEME_(280,290]_3' | id == '2020_September_EPI_CEME_(30,40]_2.2' | id == '2020_September_EPI_CEME_(90,100]_1.6' | id == '2020_September_EPI_CEME_(80,90]_2.4' | id == '2020_September_EPI_CEME_(70,80]_1.5' | id == '2020_September_EPI_CEME_(60,70]_2.2' | id == '2020_September_EPI_CEME_(50,60]_1.2' | id == '2019_December_EPI_CEME_(40,50]_4' | id == '2019_December_EPI_CEME_(350,360]_7')

seg.adfa.subset.p <- seg.adfa.subset %>% 
  group_by(gr) %>% 
  summarise(PC1 = mean(PC1), PC2 = mean(PC2), tti = mean(tti), prop.ignite.bins10_nodate = mean(prop.ignite.bins10_nodate), gti = mean(gti), fh = mean(fh), temp.max = mean(temp.max), fd = mean(fd), gd = mean(gd), pfg = mean(pfg), ttfg = mean(ttfg), lfm = mean(lfm))
```

## PV Data, TLP
Getting PV data, TLP stuff all ready for segmented regression visualizations (comparing breakpoint in segmented regression to turgor loss point derived from pressure-volume curves)

```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"))

pv_local <- pv_summary_df_timing %>% 
  filter(spp %in% c("ADFA", "CEME"))
```

```{r}
mean_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()

upr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()

lwr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()

mean_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()

upr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr)) %>% 
  pull()

lwr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

```{r}
mean_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()

upr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()

lwr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()

mean_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()

upr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr)) %>% 
  pull()

lwr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

```{r}
scaled.mem.data.alldates.noNAs <- scaled.mem.data.alldates %>% 
  drop_na(mpa, lfm, PC1)

tmp <- scaled.mem.data.alldates.noNAs %>% 
  mutate(tlp = case_when(
    spp == "ADFA" ~ mean_mpa_adfa, 
    spp == "CEME" ~ mean_mpa_ceme
  )) %>% 
  mutate(tlp_split = case_when(
    mpa > tlp ~ "tlp_above", 
    mpa < tlp ~ "tlp_below"
  )) 
tmp
```

# Global Options: Colors, Themes
```{r}
th <- theme(panel.background = element_rect(fill='white', colour='black'), # Make background white and border black
          panel.grid.major = element_blank(),  # Hide major gridlines
          panel.grid.minor = element_blank())

th.spp.wrap <- theme(legend.position = "bottom", 
        strip.text = element_text(face = "italic", size = 12) +
  scale_color_manual(values=met.brewer("Morgenstern", 7)))

Morgenstern = list(c("#7c668c", "#b08ba5", "#dfbbc8", "#ffc680", "#ffb178", "#db8872", "#a56457"), c(7, 5, 4, 6, 3, 2, 1), colorblind=TRUE)
```


# Function: Segmented Regression Visualization
```{r}
segplot <- function(data, x, y, z, tlp_value, lwr, upr, lwr_seg, upr_seg) {
  ggplot(data, aes({{x}}, {{y}})) +
  geom_point()+
  geom_line(aes({{x}}, {{z}}), #segmented line
            color = "blue2") +
  geom_vline(xintercept = tlp_value, #tlp value line
             color = "gold1") +
  geom_ribbon(aes(xmin=lwr, xmax=upr), #tlp CI ribbon
              alpha = .3,
              color = "gold1") +
  geom_vline(xintercept = lwr_seg, #segmented CI line lower
             color = "blue2")+
  geom_vline(xintercept = upr_seg, #segmented CI line upper
             color = "blue2") +
  geom_ribbon(aes(xmin=lwr_seg, xmax=upr_seg), #segmented ribbon
              alpha = .3, 
              color = "blue2") +
   th #theme!
}
```
# ----------------------------------
# Start of Segmented Regressions
# ----------------------------------

# - Live Fuel Moisture -
# PC1

#### ADFA
```{r}
out.lm<-lm(PC1 ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# Result: insignificant (p = 0.0888)

segmented.mod <-segmented(out.lm, seg.Z = ~lfm, npsi = 1) #1 breakpoint for lfm
segmented.mod
summary(segmented.mod)

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$PC1, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, PC1, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

#### CEME

```{r}
out.lm<-lm(PC1 ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# Result: marginally insignificant (p = 0.05644)

segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$PC1, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, PC1, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# PC2

#### ADFA
```{r}
out.lm<-lm(PC2 ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# Result: significant (p = 0.0142)

segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$PC1, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, PC2, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

#### CEME

```{r}
out.lm<-lm(PC2 ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# Result: significant (p = 0.02631)

segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)


confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$PC1, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, PC2, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# Prop. Ignited (10% Bins)
## ADFA
```{r}
out.lm<-lm(prop.ignite.bins10_nodate ~ lfm, data = seg.adfa.subset.p) 
davies.test(out.lm, ~lfm, k = 50)
# Highly significant (p < 0.00005)

segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod

confint(segmented.mod)

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$prop.ignite.bins10_nodate, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

segplot(seg.adfa.subset.p, lfm, prop.ignite.bins10_nodate, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

## CEME
```{r}
out.lm<-lm(prop.ignite.bins10_nodate ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: marginally significant (p = 0.04587)

segmented.mod <-segmented(out.lm, npsi = 1) #1 breakpoint for x
segmented.mod
summary(segmented.mod)

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$prop.ignite.bins10_nodate, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, prop.ignite.bins10_nodate, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# TTI

### ADFA
```{r}
out.lm<-lm(tti ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: significant

segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$tti, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, tti, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```
### CEME

```{r}
out.lm<-lm(tti ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# Result: highly significant (p = 0.0009369)

segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod
summary(segmented.mod)

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$tti, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, tti, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```


# FD

### ADFA

```{r}
out.lm<-lm(fd ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k=50)
#Result: insignificant (p = 0.6856)

segmented.mod <-segmented(out.lm, seg.Z = ~lfm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$fd, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, fd, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

### CEME
```{r}
out.lm<-lm(fd ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: insignificant (p = 0.4814)

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$fd, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, fd, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# FH

### ADFA

```{r}
out.lm<-lm(fh ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# result: significant (p = 0.001313)

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$fh, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, fh, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
out.lm<-lm(fh ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: significant (p = 0.03032)

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$fh, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, fh, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# GD

### ADFA
```{r}
out.lm<-lm(gd ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# result: insignificant

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$gd, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, gd, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
seg.ceme.subset.p.gd <- seg.ceme.subset.p %>% 
  filter(gd < 360) #Removing unrealistic glow durations
```


```{r}
out.lm <- lm(gd ~ lfm, data = seg.ceme.subset.p.gd)
davies.test(out.lm, ~lfm, k = 50)
#Result: insignificant

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p.gd$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p.gd$gd, seg.ceme.subset.p.gd$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p.gd, lfm, gd, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```


# GTI
No significant thresholds identified
### ADFA
```{r}
out.lm<-lm(gti ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# result: insignificant

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$gti, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, gti, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
out.lm <- lm(gti ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: insignificant

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$gti, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, gti, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# PFG
### ADFA
```{r}
out.lm<-lm(pfg ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# result: insignificant

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$pfg, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, pfg, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)

```

### CEME
```{r}
out.lm <- lm(pfg ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: marginally insignificant (p = 0.0667)

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$pfg, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, pfg, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```



# Max. Temp.
### ADFA
```{r}
out.lm<-lm(temp.max ~ lfm, data = seg.adfa.subset.p)
davies.test(out.lm, ~lfm, k = 50)
# result: insignificant

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$temp.max, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, temp.max, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

### CEME
```{r}
out.lm <- lm(temp.max ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: significant (p = 0.000395)

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$temp.max, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, temp.max, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```

# TTFG

### ADFA
For time to first glow, there is one strange value remaining where it probably didn't glow or didn't ignite (ttfg = 490)
```{r}
seg.adfa.subset.p.ttfg <- seg.adfa.subset.p %>% 
  filter(ttfg < 300)
```

```{r}
out.lm<-lm(ttfg ~ lfm, data = seg.adfa.subset.p.ttfg)
davies.test(out.lm, ~lfm, k = 50)
# result: insignificant

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.adfa.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.adfa.subset.p$ttfg, seg.adfa.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.adfa.subset.p, lfm, ttfg, fit, mean_lfm_adfa, lwr_lfm_adfa, upr_lfm_adfa, lower, upper)
```

### CEME
```{r}
out.lm <- lm(ttfg ~ lfm, data = seg.ceme.subset.p)
davies.test(out.lm, ~lfm, k = 50)
#Result: significant (p = 0.005595)

segmented.mod <-segmented(out.lm) #1 breakpoint for x
segmented.mod

confint <- confint(segmented.mod)
confint

lower <- confint[2]
lower

upper <- confint[3]
upper

fit <- numeric(length(seg.ceme.subset.p$lfm)) * NA

fit[complete.cases(rowSums(cbind(seg.ceme.subset.p$ttfg, seg.ceme.subset.p$lfm)))] <- broken.line(segmented.mod)$fit

segplot(seg.ceme.subset.p, lfm, ttfg, fit, mean_lfm_ceme, lwr_lfm_ceme, upr_lfm_ceme, lower, upper)
```