---
title: "Comparing Linear MEM with Segmented Regressions"
author: "Indra Boving & Joe Celebrezze"
date: "7/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r}
#lots of extra here, but oh well... 
library(ggplot2)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(ggpubr)
library(segmented)
library(lmerTest)
library(ggeffects)  # install the package first if you haven't already, then load it
library(psych)
library(sjPlot) # table functions
library(lme4) # fitting models
library(here)
library(sjstats) #use for r2 functions
select = dplyr::select
here = here::here
filter = dplyr::filter
mutate = dplyr::mutate
library(nlme)
library(remef)
library(kableExtra)
```

# 1. Data wrangling
Reading in dataframe
```{r}
scaled.mem.data.alldates.noNAs <- read.csv(here('processed-data', 'mem.data.subset.alldates.csv'))
```

Species split
```{r}
mem.data.ceme <- scaled.mem.data.alldates.noNAs %>% 
  filter(spp == "CEME")

mem.data.adfa <- scaled.mem.data.alldates.noNAs %>% 
  filter(spp == "ADFA")
```

# 2. PC1: Model Comparison

## ADFA

### Mixed Effects Models
```{r}
m1.pa <- lme(PC1~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)

m2.pa <- lme(PC1~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)

m3 <- lme(PC1~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m4 <- lme(PC1~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m5 <- lme(PC1~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.adfa)
```

Table
```{r}
tab_model(m1.pa, m2.pa, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','ADFA.PC1.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(PC1~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)
os.m1.pa<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.pa)
#AIC: 997.4369

s.m2<-lme(PC1~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)
os.m2.pa<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.pa)
#AIC: 1015.843

s.m3<-lme(PC1~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
#os.m3.pa<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
#summary.segmented(os.m3.pa)
#AIC: NA, error occurred

s.m4<-lme(PC1~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m4.pa<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4.pa)
#AIC: 1013.969
```

## CEME

### Mixed Effects Models
```{r}
m1.pc <- lme(PC1~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)

m2.pc <- lme(PC1~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)

m3 <- lme(PC1~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m4 <- lme(PC1~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m5 <- lme(PC1~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.ceme)
```

Table
```{r}
tab_model(m1.pc, m2.pc, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','CEME.PC1.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(PC1~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)
os.m1.pc<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.pc)
#AIC: 677.2741

s.m2<-lme(PC1~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)
os.m2.pc<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.pc)
#AIC: 677.3073

s.m3<-lme(PC1~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 677.6505

s.m4<-lme(PC1~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 681.1898
```

# 3. TTI: Model Comparison
## ADFA

### Mixed Effects Models
```{r}
m1.ta <- lme(tti~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)

m2.ta <- lme(tti~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)

m3 <- lme(tti~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m4 <- lme(tti~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m5 <- lme(tti~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.adfa)
```

Table
```{r}
tab_model(m1.ta, m2.ta, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','ADFA.tti.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(tti~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)
os.m1.ta<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.ta)
#AIC: 1937.612t

s.m2<-lme(tti~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)
os.m2.ta<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.ta)
#AIC: 1967.475

s.m3<-lme(tti~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 1961.825

s.m4<-lme(tti~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 1980.427
```

## CEME

### Mixed Effects Models
```{r}
m1.tc <- lme(tti~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)

m2.tc <- lme(tti~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)

m3 <- lme(tti~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m4 <- lme(tti~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m5 <- lme(tti~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.ceme)
```

Table
```{r}
tab_model(m1.tc, m2.tc, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','CEME.tti.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(tti~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)
os.m1.tc<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.tc)
#AIC: 1381.347

s.m2<-lme(tti~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)
os.m2.tc<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.tc)
#AIC: 1392.99

s.m3<-lme(tti~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 1389.266

s.m4<-lme(tti~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 1406.177
```

# 4. FH: Model Comparison

## ADFA

### Mixed Effects Models
```{r}
m1.fha <- lme(fh~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)

m2.fha <- lme(fh~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)

m3 <- lme(fh~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m4 <- lme(fh~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m5 <- lme(fh~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.adfa)
```

Table
```{r}
tab_model(m1.fha, m2.fha, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','ADFA.fh.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(fh~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)
os.m1.fha<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.fha)
#AIC: 1479.476

s.m2<-lme(fh~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)
os.m2.fha<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.fha)
#AIC: 1490.198

s.m3<-lme(fh~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 1487.758

s.m4<-lme(fh~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 1495.72
```

## CEME

### Mixed Effects Models
```{r}
m1.fhc <- lme(fh~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)

m2.fhc <- lme(fh~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)

m3 <- lme(fh~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m4 <- lme(fh~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m5 <- lme(fh~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.ceme)
```

Table
```{r}
tab_model(m1.fhc, m2.fhc, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','CEME.fh.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(fh~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)
os.m1.fhc<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.fhc)
#AIC: 1028.431

s.m2<-lme(fh~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)
os.m2.fhc<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.fhc)
#AIC: 1027.519

s.m3<-lme(fh~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 1037.788

# MODEL 4 DOES NOT WORK
```

# 5. GD: Model Comparison
## ADFA

### Mixed Effects Models
```{r}
m1.ga <- lme(gd~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)

m2.ga <- lme(gd~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)

m3 <- lme(gd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m4 <- lme(gd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m5 <- lme(gd~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.adfa)
```

Table
```{r}
tab_model(m1.ga, m2.ga, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','ADFA.gd.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(gd~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)
os.m1.ga<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.ga)
#AIC: 2407.953

s.m2<-lme(gd~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)
os.m2.ga<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.ga)
#AIC: 2405.708

s.m3<-lme(gd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 2408.069

s.m4<-lme(gd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 2401.975
```

## CEME

### Mixed Effects Models
```{r}
m1.gc <- lme(gd~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)

m2.gc <- lme(gd~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)

m3 <- lme(gd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m4 <- lme(gd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m5 <- lme(gd~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.ceme)
```

Table
```{r}
tab_model(m1.gc, m2.gc, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','CEME.gd.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(gd~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)
os.m1.gc<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.gc)
#AIC: 1737.204

s.m2<-lme(gd~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)
os.m2.gc<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.gc)
#AIC: 1737.134

s.m3<-lme(gd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 1732.315

s.m4<-lme(gd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 1733.556
```

# 6. FD: Model Comparison
## ADFA

### Mixed Effects Models
```{r}
m1.fda <- lme(fd~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)

m2.fda <- lme(fd~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)

m3 <- lme(fd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m4 <- lme(fd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)

m5 <- lme(fd~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.adfa)
```

Table
```{r}
tab_model(m1.fda, m2.fda, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','ADFA.fd.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(fd~ mpa + year.month + site, random=~1|id, data=mem.data.adfa)
os.m1.fda<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.fda)
#AIC: 1513.617

s.m2<-lme(fd~ lfm + year.month + site, random=~1|id, data=mem.data.adfa)
os.m2.fda<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.fda)
#AIC: 1514.792

s.m3<-lme(fd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 1513.072

s.m4<-lme(fd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.adfa)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 1513.666
```

## CEME

### Mixed Effects Models
```{r}
m1.fdc <- lme(fd~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)

m2.fdc <- lme(fd~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)

m3 <- lme(fd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m4 <- lme(fd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)

m5 <- lme(fd~ mpa + dw.flam.sample + sample.wt + year.month + site, random=~1|id, data=mem.data.ceme)
```

Table
```{r}
tab_model(m1.fdc, m2.fdc, m3, m4, m5,
          show.reflvl = FALSE, 
          digits = 3, 
          show.aic = TRUE, 
          show.ci = FALSE,
          show.icc = FALSE, 
          pred.labels = c(),
         dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
         string.pred = "Coeffcient", 
         title = "models with no collinearity",
  string.p = "P-Value", 
  p.style = "stars",
  file = here('figures', 'MEM.figures','CEME.fd.MEM.html')) # saving .html into figures folder
```

### Segmented Regressions
```{r}
s.m1<-lme(fd~ mpa + year.month + site, random=~1|id, data=mem.data.ceme)
os.m1.fdc<-segmented.default(s.m1, ~mpa, npsi=list(mpa=1))
summary.segmented(os.m1.fdc)
#AIC: 1053.864

s.m2<-lme(fd~ lfm + year.month + site, random=~1|id, data=mem.data.ceme)
os.m2.fdc<-segmented.default(s.m2, ~lfm, npsi=list(lfm=1))
summary.segmented(os.m2.fdc)
#AIC: 1052.68

s.m3<-lme(fd~ ww.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m3<-segmented.default(s.m3, ~ww.flam.sample, npsi=list(ww.flam.sample=1))
summary.segmented(os.m3)
#AIC: 1054.502

s.m4<-lme(fd~ dw.flam.sample + year.month + site, random=~1|id, data=mem.data.ceme)
os.m4<-segmented.default(s.m4, ~dw.flam.sample, npsi=list(dw.flam.sample=1))
summary.segmented(os.m4)
#AIC: 1052.069
```

#-----------------------------------

# Summary Table
```{r}
fix.fx <- c(rep(c("Water Potential", "Water Potential", "Live Fuel Moisture", "Live Fuel Moisture"), 10))

aic.values <- AIC(m1.pa, os.m1.pa, m2.pa, os.m2.pa, m1.pc, os.m1.pc, m2.pc, os.m2.pc, m1.ta, os.m1.ta, m2.ta, os.m2.ta, m1.tc, os.m1.tc, m2.tc, os.m2.tc, m1.fha, os.m1.fha, m2.fha, os.m2.fha, m1.fhc, os.m1.fhc, m2.fhc, os.m2.fhc, m1.ga, os.m1.ga, m2.ga, os.m2.ga, m1.gc, os.m1.gc, m2.gc, os.m2.gc, m1.fda, os.m1.fda, m2.fda, os.m2.fda, m1.fdc, os.m1.fdc, m2.fdc, os.m2.fdc)$AIC

diff.aic <- AIC(m1.pa, m2.pa, m1.pc, m2.pc, m1.ta, m2.ta, m1.tc, m2.tc, m1.fha, m2.fha, m1.fhc, m2.fhc, m1.ga, m2.ga, m1.gc, m2.gc, m1.fda, m2.fda, m1.fdc, m2.fdc)$AIC - AIC(os.m1.pa, os.m2.pa, os.m1.pc, os.m2.pc, os.m1.ta, os.m2.ta, os.m1.tc, os.m2.tc, os.m1.fha, os.m2.fha, os.m1.fhc, os.m2.fhc, os.m1.ga, os.m2.ga, os.m1.gc, os.m2.gc, os.m1.fda, os.m2.fda, os.m1.fdc, os.m2.fdc)$AIC 
diff.aic

d.aic <- c('7.62504980', " ", '-0.02300228', " ", '-0.07314890', " ",  '6.35947790', " ", '14.46551012', " ",  '12.17356390', " ",  '3.19816683', " ",  '22.20671746', " ",  '3.88609038', " ",  '7.99002428', " ",  '17.48653269', " ",  '14.59977267', " ",  '8.60958029', " ",  '7.51919544', " ",  '8.62388566', " ",  '7.11361267', " ",  '3.32824736', " ",  '2.39598947', " ",  '3.75932306', " ",  '2.18676268', ' ')

bic.values <- BIC(m1.pa, os.m1.pa, m2.pa, os.m2.pa, m1.pc, os.m1.pc, m2.pc, os.m2.pc, m1.ta, os.m1.ta, m2.ta, os.m2.ta, m1.tc, os.m1.tc, m2.tc, os.m2.tc, m1.fha, os.m1.fha, m2.fha, os.m2.fha, m1.fhc, os.m1.fhc, m2.fhc, os.m2.fhc, m1.ga, os.m1.ga, m2.ga, os.m2.ga, m1.gc, os.m1.gc, m2.gc, os.m2.gc, m1.fda, os.m1.fda, m2.fda, os.m2.fda, m1.fdc, os.m1.fdc, m2.fdc, os.m2.fdc)$BIC

diff.bic <- BIC(m1.pa, m2.pa, m1.pc, m2.pc, m1.ta, m2.ta, m1.tc, m2.tc, m1.fha, m2.fha, m1.fhc, m2.fhc, m1.ga, m2.ga, m1.gc, m2.gc, m1.fda, m2.fda, m1.fdc, m2.fdc)$BIC - BIC(os.m1.pa, os.m2.pa, os.m1.pc, os.m2.pc, os.m1.ta, os.m2.ta, os.m1.tc, os.m2.tc, os.m1.fha, os.m2.fha, os.m1.fhc, os.m2.fhc, os.m1.ga, os.m2.ga, os.m1.gc, os.m2.gc, os.m1.fda, os.m2.fda, os.m1.fdc, os.m2.fdc)$BIC
diff.bic

d.bic <- c('0.60528351', " ", '-7.04276857', " ", '-6.37014193', " ", '0.06248487', " ",  '7.44574383', " ", '5.15379761', " ", '-3.09882621', " ", '15.90972443', " ", '-3.13367591', " ", '0.97025799', " ", '11.18953965', " ", '8.30277964', " ", '1.58981400', " ", '0.49942914', " ",    '2.32689262', " ", '0.81661963', " ", '-3.69151893', " ", '-4.62377682', " ", '-2.53766998', " ",  '-4.11023036', " ")

dep.var <- c("PC1", " ", " ", " ", " ", " ", " ", " ", "Time to Ignition (s)", " ", " ", " "," ", " ", " ", " ", "Flame Height (cm)", " ", " ", " "," ", " ", " ", " ", "Glow Duration (s)", " ", " ", " "," ", " ", " ", " ", "Flame Duration (s)", " ", " ", " "," ", " ", " ", " ")

sp.lab <- c("ADFA", " ", " ", " ", "CEME", " ", " ", " ", "ADFA", " ", " ", " ", "CEME", " ", " ", " ", "ADFA", " ", " ", " ", "CEME", " ", " ", " ", "ADFA", " ", " ", " ", "CEME", " ", " ", " ", "ADFA", " ", " ", " ", "CEME", " ", " ", " ")

an.lab <- c(rep(c("Linear MEM", "Segmented Regression"), 20))
```

```{r}
mem.vs.seg.table.df <- data.frame(dep.var, sp.lab, an.lab, fix.fx, aic.values, d.aic, bic.values, d.bic)

mem.vs.seg.table.df %>%
  kable(format = 'html', escape = F, col.names = c('Dependent Variable', 'Species', 'Analysis', 'Model Fixed Effects', 'AIC', 'Change in AIC', 'BIC', 'Change in BIC')) %>% 
  kable_styling(bootstrap_options = c('hover', 'bordered', 'condensed'), fixed_thead = T) %>% 
  row_spec(c(1, 9, 17, 25, 33), background = "#D3D3D3") %>% 
  save_kable(here('figures', 'extra-figures', 'MEM_vs_SegReg_kable.html'))
```
