---
title: "Extra/Supplemental Figures"
author: "Indra Boving & Joe Celebrezze"
date: "6/21/2022"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#lots of extra here, but oh well... 
library(ggplot2)
library(gapminder)
library(data.table)
library(purrr) #for visualizing all variables in one big plot
library(naniar) #for dealing with NAs nicely 
library(tidyverse)
library(devtools)
library(ggfortify)
library(ggpubr)
library(jtools)
library(cowplot)
library(lmerTest)
library(ggeffects)  # install the package first if you haven't already, then load it
library(GGally) #for corr plots
require(kimisc) # has the nlist function to create a named list
require(AICcmodavg) # has the aictab function
library(psych)
#devtools::install_github("strengejacke/strengejacke")
library(strengejacke)
library(sjPlot) # table functions
library(sjmisc) # sample data
library(lme4) # fitting models
library(here)
library(effects) #for plotting model effects
library(sjstats) #use for r2 functions
library(TMB)
library(glmmTMB)
library(lattice)
library(equatiomatic)
library("broom.mixed")
library(ggbiplot)
select = dplyr::select
here = here::here
library(MuMIn)
library(modelsummary)
#install_github("BlakeRMills/MetBrewer") 
#library("BlakeRMills/MetBrewer")
library(segmented)
filter = dplyr::filter
mutate = dplyr::mutate
library(nlme)
library(MetBrewer)
#install.packages("segmented")
#devtools::install_github("hohenstein/remef")
library(remef)
```

Set global options for color palettes and themes: 

```{r}
th <- theme(panel.background = element_rect(fill='white', colour='black'), # Make background white and border black
          panel.grid.major = element_blank(),  # Hide major gridlines
          panel.grid.minor = element_blank())

th.spp.wrap <- theme(legend.position = "bottom", 
        strip.text = element_text(face = "italic", size = 12) +
  scale_color_manual(values=met.brewer("Morgenstern", 7)))

Morgenstern = list(c("#7c668c", "#b08ba5", "#dfbbc8", "#ffc680", "#ffb178", "#db8872", "#a56457"), c(7, 5, 4, 6, 3, 2, 1), colorblind=TRUE)
```

#------------------------------------
# 1. Data wrangling

Seasonal mins and maxs from 2016 - 2020:

https://www.sbbg.org/about/onsite-weather-station-live-fuel-moisture 

```{r}
adfa_min <- 55
adfa_max <- 110

ceme_min <- 55
ceme_max <- 140
```

### All dates datasets
```{r, message=FALSE, warning=FALSE, include=FALSE}
mem.data.alldates <- read_csv(here("processed-data", "mem.data.local.epi.alldates.csv"), show_col_types = FALSE)

mem.data.raw.alldates <- mem.data.alldates %>%
  mutate(mpa = case_when(
    mpa > 0 ~ (-1*mpa), 
    mpa < 0 ~ mpa)) %>% 
  mutate(year = as.factor(year)) %>%
  mutate(month = as.factor(month)) %>% 
  mutate(mpa.unscaled = mpa) %>% 
  mutate(lfm.unscaled = lfm)%>% 
  mutate(lfm.NAs.imputed.unscaled = lfm.NAs.imputed) %>% 
  mutate(excess_water.scaled = ww.flam.sample - dw.flam.sample) %>% 
  mutate(excess_water.unscaled = excess_water.scaled)
 # mutate(lfm = lfm.NAs.imputed)

clean.mem.data.alldates <- mem.data.raw.alldates
  #na.omit() %>%
  #filter(year.month == "2020_September")

#Parsing out the variables of interest for the mixed effects modelling

clean.mem.data.dependant.alldates <- clean.mem.data.alldates[,c('PC1', 'PC2', 'PC3', 'PC4', 'tti', 'fh', 'gd', 'fd','temp.max', 'flam.index', 'year', 'month', 'prop.ignite', 'prop.ignite.bins5', "ignition")]
 
scaled.mem.data.predictors.alldates.adfa <- clean.mem.data.alldates %>%
  filter(spp == "ADFA") %>% 
  dplyr::select('lfm.NAs.imputed', 'lfm.outliers.out', 'mpa', 'dw.flam.sample', 'sample.wt', 'ww.flam.sample', 'lfm', 'excess_water.scaled') %>%
 scale()

  
scaled.mem.data.predictors.alldates.ceme <- clean.mem.data.alldates %>%
  filter(spp == "CEME") %>% 
  dplyr::select('lfm.NAs.imputed', 'lfm.outliers.out', 'mpa', 'dw.flam.sample', 'sample.wt', 'ww.flam.sample', 'lfm', 'excess_water.scaled') %>%
 scale()
  
scaled.mem.data.predictors.alldates <- rbind(scaled.mem.data.predictors.alldates.adfa, scaled.mem.data.predictors.alldates.ceme)

mem.data.predictors.alldates <- clean.mem.data.alldates %>%
    dplyr::select('spp', 'year.month', 'individual', 'site', 'start.temp', 'precip.2mo','mpa.unscaled', 'lfm.unscaled', 'lfm.NAs.imputed.unscaled', 'excess_water.unscaled', 'hydration', 'gr') 

scaled.mem.data.alldates <- cbind(scaled.mem.data.predictors.alldates, 
                         mem.data.predictors.alldates,
                         clean.mem.data.dependant.alldates) 

#For sept. 2020 only: 
scaled.mem.data.alldates <- scaled.mem.data.alldates %>% 
  mutate(Species = case_when(
    spp == "ADFA" ~ "Adenostoma fasciculatum", 
    spp == "CEME" ~ "Ceanothus megacarpus"
  )) %>% 
  mutate(id = individual)  %>% 
  mutate(timing = case_when(
    year.month == "2016_December" ~ "Dec. 2016", 
    year.month == "2019_December" ~ "Dec. 2019",
    year.month == "2018_January" ~ "Jan. 2018",
    year.month == "2020_January" ~ "Jan. 2020",
    year.month == "2020_September" ~ "Sept. 2020"
  ))

scaled.mem.data.alldates.noNAs <- scaled.mem.data.alldates %>% 
  drop_na(mpa, lfm, PC1, timing, mpa.unscaled, lfm.unscaled)

seg.data.subset.alldates <- scaled.mem.data.alldates.noNAs %>% 
  mutate(id = individual) 

seg.data.subset.alldates<-seg.data.subset.alldates[order(seg.data.subset.alldates$id),]
```


```{r, message=FALSE, warning=FALSE, include=FALSE}
seg.adfa.subset <- seg.data.subset.alldates  %>% 
  filter(spp == "ADFA") %>% 
  filter(ignition == "1")

seg.CEME.subset <- seg.data.subset.alldates  %>% 
  filter(spp == "CEME")%>% 
  filter(ignition == "1")

seg.adfa.subset.allignitions <- seg.data.subset.alldates  %>% 
  filter(spp == "ADFA")

seg.CEME.subset.allignitions <- seg.data.subset.alldates %>% 
  filter(spp == "CEME")

seg.adfa.subset.limited <- seg.adfa.subset %>% 
  filter(lfm.unscaled < adfa_max, lfm.unscaled > adfa_min)

seg.CEME.subset <- seg.data.subset.alldates %>% 
  filter(spp == "CEME")

seg.CEME.subset.limited <- seg.CEME.subset %>% 
  filter(lfm.unscaled < ceme_max, lfm.unscaled > ceme_min)
```

Scale LFM based on sample data: 
```{r}
scaled.mem.data.alldates.noNAs <- scaled.mem.data.alldates.noNAs %>%
  group_by(year.month) %>% 
  mutate(lfm.scaled.by.year = scale(lfm), 
         mpa.scaled.by.year = scale(mpa))

```

Labels for species names:
```{r}
spp.labs <- c("Adenostoma fasciculatum", "Ceanothus megacarpus")
names(spp.labs) <- c("ADFA", "CEME")
```

#------------------------------------
# 2. LFM vs. TTI, FH, GD

```{r}
tti <- ggplot() + 
  geom_point(data= scaled.mem.data.alldates.noNAs, aes(lfm.scaled.by.year, tti, color = Species), size = .5) + 
  geom_smooth(method = "lm", 
              data= scaled.mem.data.alldates.noNAs, 
              aes(lfm.scaled.by.year, tti, color = Species), se = FALSE, size = .7) +
  #geom_line(data=x_mpa_fig, aes(x=lfm, y=fit), color="#7570b3") +
  #geom_ribbon(data= x_mpa_fig, aes(x=lfm, ymin=lower, ymax=upper), alpha= 0.3, fill="#7570b3") +
  labs(
    #x="Live Fuel Moisture (%)", 
       y="Time to Ignition (sec)")  +
  scale_color_manual(values = c("#b08ba5", "#ffb178")) +
  th +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.x=element_blank(),
        legend.position = "none") 
tti
```


```{r}
fh <- ggplot() + 
  geom_point(data= scaled.mem.data.alldates.noNAs, aes(lfm, fh, color = Species), size = .5) + 
  #geom_point(data=x_mpa_fig, aes(x=lfm, y=fit), color="#7570b3", size = 1) +
  #geom_line(data=x_mpa_fig, aes(x=lfm, y=fit), color="#7570b3") +
  geom_smooth(method = "lm", data= scaled.mem.data.alldates.noNAs, aes(lfm, fh, color = Species), se = FALSE, size = .7) +
  #geom_ribbon(data= x_mpa_fig, aes(x=lfm, ymin=lower, ymax=upper), alpha= 0.3, fill="#7570b3") +
  labs(
    #x="Live Fuel Moisture (%)", 
       y="Flame Height (cm)")  +
  scale_color_manual(values = c("#b08ba5", "#ffb178")) +
  th +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(), 
        axis.title.x=element_blank(),
        legend.position = "none") 
fh
```


```{r}
gd <- ggplot() + 
  geom_point(data= scaled.mem.data.alldates.noNAs, aes(lfm, gd, color = Species), size = .5) + 
  #geom_point(data=x_mpa_fig, aes(x=lfm, y=fit), color="#7570b3", size = 1) +
  #geom_line(data=x_mpa_fig, aes(x=lfm, y=fit), color="#7570b3") +
  geom_smooth(method = "lm", data= scaled.mem.data.alldates.noNAs, aes(lfm, gd, color = Species), se = FALSE, size = .7) +
  #geom_ribbon(data= x_mpa_fig, aes(x=lfm, ymin=lower, ymax=upper), alpha= 0.3, fill="#7570b3") +
  labs(x="Live Fuel Moisture (%)", 
       y="Glow Duration (sec)")  +
  scale_color_manual(values = c("#b08ba5", "#ffb178")) +
  th +
  theme(legend.title = element_text(size = 10), 
        legend.text = element_text(size = 8), 
        legend.position = "bottom")
gd
```


```{r, fig1, fig.height = 6, fig.width = 3}
cowplot::plot_grid(tti, fh, gd, 
          ncol = 1)

ggsave(here('figures', 'lfm.vs.flam.metrics.jpg'))
```
#------------------------------------
# 3. More data wrangling 

## PV data

```{r}
pv_summary_df_timing <- read_csv(here("processed-data", "pv_summary_df_timing.csv"))

pv_local <- pv_summary_df_timing %>% 
  filter(spp %in% c("ADFA", "CEME"))
```

## Prop.ignite v LFM: 10% 
```{r}
dlookr::diagnose(seg.adfa.subset)
```

```{r}
library(tidyverse)

mean_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()

upr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()

lwr_lfm_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()

mean_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()

upr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(upr)) %>% 
  pull()

lwr_mpa_adfa <- pv_local %>% 
  filter(spp == "ADFA") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

```{r}
mean_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_lfm)) %>% 
  pull()

upr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr_lfm)) %>% 
  pull()

lwr_lfm_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr_lfm)) %>% 
  pull()

mean_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(mean_tlp)) %>% 
  pull()

upr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(upr)) %>% 
  pull()

lwr_mpa_ceme <- pv_local %>% 
  filter(spp == "CEME") %>% 
  summarise(mean(lwr)) %>% 
  pull()
```

```{r}
tmp <- scaled.mem.data.alldates.noNAs %>% 
  mutate(tlp = case_when(
    spp == "ADFA" ~ mean_mpa_adfa, 
    spp == "CEME" ~ mean_mpa_ceme
  )) %>% 
  mutate(tlp_split = case_when(
    mpa.unscaled > tlp ~ "tlp_above", 
    mpa.unscaled < tlp ~ "tlp_below"
  )) 
tmp
```

#------------------------------------
# 4. Boxplots
## 4.1 Pre/Post TLP
### Prop. Ignite
```{r}
tmp %>% 
  ggplot(aes(y = prop.ignite.bins5, x = lfm.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```

```{r}
tmp %>% 
  ggplot(aes(y = prop.ignite.bins5, x = mpa.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```
### PC1

```{r}
tmp %>% 
  ggplot(aes(y = PC1, x = lfm.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```
```{r}
tmp %>% 
  ggplot(aes(y = PC1, x = mpa.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```

### TTI

```{r}
tmp %>% 
  ggplot(aes(y = tti, x = lfm.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```

```{r}
tmp %>% 
  ggplot(aes(y = tti, x = mpa.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```

### FD

```{r}
tmp %>% 
  ggplot(aes(y = fd, x = lfm.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```

### FH

```{r}
tmp %>% 
  ggplot(aes(y = fh, x = lfm.unscaled, fill = tlp_split)) +
  facet_wrap(~spp) +
  geom_boxplot()
```

## 4.2 PC1 vs. LFM bins
Filtering out only realistic LFM values
Reordering factors so the LFM bins go in order
```{r}
seg.data.subset.limited <- seg.data.subset.alldates %>% 
  filter(lfm.unscaled > 50 & lfm.unscaled < 160) %>% 
  mutate(gr = factor(gr, levels=c('(50,60]', '(60,70]', '(70,80]','(80,90]', '(90,100]', '(100,110]', '(110,120]', '(120,130]', '(130,140]', '(140,150]', '(150,160]')))
```

Boxplot split by species
```{r}
ggplot(data = seg.data.subset.limited, aes(x = gr, y = PC1)) +
  geom_boxplot() +
  facet_wrap(~spp, ncol = 1) +
  th
```

Violin plot
```{r}
ggplot(data = seg.data.subset.limited, aes(x = gr, y = PC1)) +
  geom_violin() +
  facet_wrap(~spp, ncol = 1) +
  th
```

#------------------------------------
# 5. Field Data

```{r}
field_data_local <- read.csv(here("raw-data", "local_field_data.csv")) %>% 
  janitor::clean_names() %>% 
  filter(spp %in% c("ADFA", "CEME")) 
  
field_data_local$date <- lubridate::mdy(field_data_local$date)

field_data_local <- field_data_local  %>% 
   mutate(month = month(date), 
          year = year(date)) %>% 
   mutate(age = case_when(
     age == "New" ~ "new", 
     age == "Old" ~ "old", 
     age == "new" ~ "new", 
     age == "old" ~ "old", 
     TRUE ~ as.character(age)
   )) 
```

Range of LFM in field data
```{r}
field_data_local %>% 
  ggplot(aes(y = lfm, x = spp, fill = spp)) +
  geom_point() +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values=c("#9D0208","#F48C06")) +
  labs(x = "Species", y = "LFM (%)", fill = "Species") +
  th

ggsave(here('figures', 'lfm.field.data.jpg'), height = 7, width = 9)
```

Comparing field measurements of water status/content
```{r}
field.plot1 <- field_data_local %>% 
  ggplot(aes(y = lfm, x = midday*-1, color = spp)) +
  geom_point() +
  labs(x = "Midday Water Potential", y = "LFM", color = "Species") + 
  scale_color_manual(values=c("#9D0208","#F48C06")) +
  th

field.plot2 <- field_data_local %>% 
  ggplot(aes(y = lfm, x = predawn*-1, color = spp)) +
  geom_point() +
  labs(x = "Predawn Water Potential", y = "LFM", color = "Species") + 
  scale_color_manual(values=c("#9D0208","#F48C06")) +
  th

field.plot3 <- field_data_local %>% 
  ggplot(aes(y = midday*-1, x = predawn*-1, color = spp)) +
  geom_point() +
  labs(x = "Predawn Water Potential", y = "Midday Water Potential", color = "Species") +
  scale_color_manual(values=c("#9D0208","#F48C06")) +
  th

ggarrange(field.plot1, field.plot2, field.plot3, ncol = 3, common.legend = TRUE)

ggsave(here('figures', 'field.plots.jpg'), height = 4, width = 12)
```
